---
title: "Update 7.1 stats added "
linktitle: "2020-08-27 Update 7.1 stats added"
date: `r today("UTC")`
publishdate: 2020-08-27
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.1"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver <- "7.1"
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Stats for `r md_link_update(update=update_ver)` have been added. Now tank pages 
are available to all tiers for current and previous main udpate version.

Premium tanks (and especially the pricey loot-box tanks) continue to 
dominate the `r md_link_tier(update=update_ver, tier=8)` tank rankings. 
13 out of 15 best performing tanks are premium tanks. Is the game slipping 
step-by-step towards _Pay-2-Win_?

```{r fig_tanks_tier8_rWR}
tank_type  	<- NULL
tierN 			<- 8
stats 			<- get_stats.update.tier(tierN = tierN, DT = stats.update.perf)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```


