---
title: "Update 7.0 stats added "
linktitle: "2020-07-16 Update 7.0 stats added"
date: `r today("UTC")`
publishdate: 2020-07-16
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.0"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = "7.0";
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Added stats for `r md_link_update(update=update_ver)`. 
Interestingly, the player base tracked played far less battles during 
the update compared to the previous update despite the update interval 
being very long due to the WG release schedule. 

## Stats per Tier / Tank type

In addition I have added stats for 
`r md_link_tier_tank_type(update=NULL, tier=8, tank_type="Heavy Tank", link_text="tank types per tier")`. 
The other pages show only top 10/20 tanks per graph, but these pages list every tank of type at the tier.


```{r fig_tanks_tier8_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 8
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```
