---
title: "Update 8.4 final stats added "
linktitle: "2021-11-19 Update 8.4 final stats added"
date: `r today("UTC")`
publishdate: 2021-11-19
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "8.4" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver <- '8.4'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were `r auto_format(res$Battles)` battles by `r auto_format(res$Players)` 
players recorded in the database during the `r md_link_update(update=update_ver)`.

New  (`r md_link_tier_premium_tank(update=update_ver, tier=8, link_text="premium")`) 
tanks have entered the 
`r md_link(update=update_ver, link_text="TOP20 best performing tanks", rel_link="#highest-relative-wr")` list. 

* Thanks to the recent promotion, `r md_link_tank(tank_names='Somua SM', update=update_ver)` 
has entered the battlefield in numbers and taken the 3rd spot. High burst damage combined with 
ultra-strong turret, good gun depression and decent mobility - what could go wrong?

* The usual suspects `r md_link_tank(tank_names='T28 Concept', update=update_ver)` 
and `r md_link_tank(tank_names='Object 252U', update=update_ver)` have taken the 
the top spots again. 

* Rather unpopular `r md_link_tank(tank_names='AT 15A', update=update_ver)` has 
dropped to 17th. I think its low player count make its relative WR stats more unreliable 
with high   update-to-update variation. 

* Dead-ugly fake-tank `r md_link_tank(tank_names='Dreadnought', update=update_ver)` 
(a buffed fantasy-copy of `r md_link_tank(tank_names='Churchill Gun Carrier', update=update_ver)` 
aka *Coffin on Tracks*) was 4th. 

* `r md_link_tank(tank_names='IS-7', update=update_ver)` received a nice buff 
during "PBR remodeling"and it is really good now and actually the best performing 
Tech-Tree tank (8th). 

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

## Polish heavy tanks

`r md_link_update(update=update_ver, capital_1st=TRUE)` introduced Polish heavy 
tanks. I have reached tier IX with those and I think all the tanks so far are fine tanks. 
Good armor, good mobility, OK gun-depression and good alpha. However, the stats of the Polish 
heavies look *"meh"* at the best. However, usually the first update's stats underestimate 
a bit the performance of new tank lines. This might be due to many players still grinding 
the tanks with stock modules and below-100% crews. I try to take the grind-time into consideration, 
but there is no certain way to filter out non-maxed out tanks. I expect the stats to improve a 
bit in next update. 

### Tier VI 40TP Habicha

The `r md_link_tier(update=update_ver, tier=6)` 
`r md_link_tank(tank_names='40TP Habicha', update=update_ver)` 
was a nice tank in my view, but based on stats it was the 3rd worst 
performing `r md_link_tier_tank_type(update=update_ver, tier=6, tank_type="Heavy Tank", append_text="heavy tank")`. 
I played only 17 battles with it (boosters, yeah) and got [70% WR](https://www.blitzstars.com/player/eu/Jylpah/tank/8065). 
I have too few battles to really say anything of my own performance with it, but it felt OK - or I got carried :-)  

```{r fig_tanks_tier6_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 6
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

### Tier VII 45TP Habicha

The `r md_link_tier(update=update_ver, tier=7)` 
`r md_link_tank(tank_names='45TP Habicha', update=update_ver)` 
was also a nice tank in my view, but based on stats it was the 2nd worst 
performing `r md_link_tier_tank_type(update=update_ver, tier=7, tank_type="Heavy Tank", append_text="heavy tank")`. 
I played 52 battles with it and did OK, although I felt fighting with windmills (teams) 
and reached only [61% WR](https://www.blitzstars.com/player/eu/Jylpah/tank/8321).   

```{r fig_tanks_tier7_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 7
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN)
```

### Tier VIII 53TP Markowskiego

The `r md_link_tier(update=update_ver, tier=8)` 
`r md_link_tank(tank_names='53TP Markowskiego', update=update_ver)` was again
a really nice tank in my view, but based on stats it is just an average performer 
among `r md_link_tier_tank_type(update=update_ver, tier=8, tank_type="Heavy Tank")`.
I played 82 battles with it and reached [64% WR](https://www.blitzstars.com/player/eu/Jylpah/tank/7809)
with it that is pretty average for me.

```{r fig_tanks_tier8_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 8
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN)
```


### Tier IX 50TP Tyszkiewicza

The `r md_link_tier(update=update_ver, tier=9)` 
`r md_link_tank(tank_names='50TP Tyszkiewicza', update=update_ver)` 
is another good tank in my view, but based on stats it is an average performer 
among `r md_link_tier(update=update_ver, tier=9)`. I have  played so 
far 110 battles with it and standing at [60% WR](https://www.blitzstars.com/player/eu/Jylpah/tank/7553) 
with it. The Gods of MM are asking more sacrifices from my wallet.

```{r fig_tanks_tier9_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 9
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN)
```

### Tier X 60TP Lewandowskiego

I have not played the `r md_link_tier(update=update_ver, tier=10)` 
`r md_link_tank(tank_names='60TP Lewandowskiego', update=update_ver)` yet,
but it does not seem to be so fearsome enemy on the battlefield. Yes, it has a great turret, 
but I have *felt* it is pretty balanced. However, based on stats it seems to be a below-average 
performer among `r md_link_tier(update=update_ver, tier=10)`. 

```{r fig_tanks_tier10_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN)
```
Let's see how the update 8.5 stats turn out once those are out. 
It is hard for me to believe this line is performing so poorly since I think the tanks are all fine. 

*That's all this time*
