---
title: "Update 7.2 stats added "
linktitle: "2020-10-11 Update 7.2 stats added"
date: `r today("UTC")`
publishdate: 2020-10-11
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.2"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver <- "7.2"
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Stats for `r md_link_update(update_ver)` have been added. 

* Record 205M battles by 456k players was recorded in the database. 
Please note, these are note all the WoT Blitz players, just those 
tracked by BlitzAnalysiz[]. 

* There seem to be more low-tier stat-padders captured in the database 
since Top 5 highest WR tanks are Tier V or below. 

```{r fig_tanks_top_averageWR}
plot_averageWR(stats = stats.update.perf, update = update_ver);
```


* `r md_link_tank(update=update_ver, tank_names="T28 Concept")`, 
`r md_link_tank(update=update_ver, tank_names="Object 252U")`  
and `r md_link_tank(update=update_ver, tank_names="Chimera")` 
continue to be the best performing tanks in the game, with 
`r md_link_tank(update=update_ver, tank_names="T54E2")` 
taking the 3rd place in front of 
`r md_link_tank(update=update_ver, tank_names="Chimera")`. 
Top four tanks are all premium tanks. It must be a pure accident by WG balancing 
department. If it were a result of conscious decision, someone could say the 
game is becoming pay-to-win...

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* Armor continues to rule in the game. The top tanks are a well-armored tanks. 
`r md_link_tier(update=update_ver, tier=10, rel_link="#the-best-performing-tanks", link_text="Tier X is dominated by tanks", capital_1st=TRUE)`
like 
`r md_link_tank(update=update_ver, tank_names="Maus")` , 
`r md_link_tank(update=update_ver, tank_names="IS-4")`, 
`r md_link_tank(update=update_ver, tank_names="T110E3")`, 
`r md_link_tank(update=update_ver, tank_names="E 100")` and 
`r md_link_tank(update=update_ver, tank_names="IS-7")`. 
Of course the _average_ Relative WR favors tanks that are easy to 
play for the _average players_. 


```{r fig_tanks_top20_tier10_RelativeWR}
tank_type  	<- NULL
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
																tank_type = tank_type, tier = tierN)
```
* And I finally managed to fix the annoying parallel processing bug that has 
taken most of my BlitzAnalysiz development time. The issue was that multi-threaded 
[OpenBLAS](https://www.openblas.net/)-libraries used by `loess()` not being 
thread-safe in multi-core applications. `library('RhcpBLASctl'); blas_set_num_threads(1)` 
took care of it. It took probably 50h to debug it. Debugging parallel code is **PIA**. 
Finally solved it! _By definition, bugs are found in the last place you are looking for those._





