---
title: "Update 7.4 final stats added "
linktitle: "2020-12-11 Update 7.4 stats added"
date: `r today("UTC")`
publishdate: 2020-12-11
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.4"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.4'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were 208M battles by 491k players recorded in the database 
during the `r md_link_update(update=update_ver)` so far. Please note, these 
are note all the WoT Blitz players, just those tracked by BlitzAnalysiz[]. 

* `r md_link_tank(tank_names='Chimera', update=update_ver)` has taken the title 
of the best performing (most OP) tank in the game and 
`r md_link_tank(tank_names='T28 Concept', update=update_ver)` 
maintained its 2nd place. In the final stats 
`r md_link_tank(tank_names='Emil I', update=update_ver)` dropped to 5th, 
but was still ahead of notoriously well-known OP tanks like 
`r md_link_tank(tank_names='Annihilator', update=update_ver)` and 
`r md_link_tank(tank_names='Object 252U', update=update_ver)`.  

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* `r md_link_tank(tank_names='Emil I', update=update_ver)` and 
`r md_link_tank(tank_names='Emil II', update=update_ver)` got nerfed in update 7.5.
 It will be in the interesting to see how will those perform during update 7.5. 

* `r md_link_tank(tank_names='Kranvagn', update=update_ver)` remains _meh_. 
Maybe the Minsk folks are not fans of Sweden and have decided to 
leave it at its bit disappointing level. 

```{r fig_tank_relativeWR_kranvagn}
tank_id     <- get_tank_id('Kranvagn')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```
