---
title: "The most OP tanks - ever"
linktitle: "2020-12-03 The most OP tanks - ever"
date: `r today("UTC")`
publishdate: 2020-12-03
author: Jylpah@gmail.com
disableToc: false
output: md_document
weight: page_weight
alwaysopen: false
hidden: true
tags: [ "post" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = c("svglite", "png"))
# Load stats
update_ver <- "7.4"
stopifnot(update_ver == update)
fn <- filename_career(update)
stats <- qread(fn)
stats <- calc_tank_stats(stats, career_stats = TRUE)
```

A fellow tanker asked a 
[simple question](http://forum.wotblitz.eu/index.php?/topic/54989-most-op-regular-tank-of-all-time/) 
of "what is the most OP _regular_ tank in Blitz of all time?". 
A fair question and something I would have not been able to guess. 

Of course the definition of the "best" is the one that decides the 
answer and I have chosen the criteria to be 
[Relative WR](/blog/2020-06-08_measuring_tank_performance/#introducing-relative-wr) 
- the average of the differences between players' WR in a tank and average WR in 
their all same tier tanks. And in this case I have calculated it over the time, 
not during the peak performance of each of the tanks. WG has launched many tank 
lines with OP tanks, but over the time most of those have been nerfed to reasonable 
levels or been power-creeped.  

# The most OP regular tanks of all times

To my surprise the most OP tank of all times is 
`r md_link_tank(tank_names='Emil I', update=update_ver)`. It is not that there never have 
been more OP regular tanks than Emil I, but those have been nerfed and 
over the time their "average OPness" had been brought under more 
reasonable levels.   


```{r fig_top20_regular_tanks_Relative_WR_all_time}
res <- head(stats[DT_filter_enough_battles.rWR(stats),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(all.battles),
    "Vehicle Class" = first(type),
    "Premium" = first(is_premium)
  ),
  by = name
][(!Premium) & (Players >= min_players.tank)][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
plot_col_discrete_2Y(res, "Top 20 Regular Tanks by Relative WR of all times", update,
  x_name, y_name, y2_name,
  fill_var = "Vehicle Class", y2_pct = FALSE
)
```

#### The most OP regular tanks of all times - Table

{{% expand "Show table" %}}
```{r top20_regular_tanks_Relative_WR_all_time, echo = FALSE}
md_table(res, update_ver = update)
```
{{% /expand %}}

# The most OP tanks of all times
##### Including premium tanks

But is `r md_link_tank(tank_names='Emil I', update=update_ver)` the most OP tank in 
the game all-time - including the premium tanks? Not even close to. 
It barely fits into the TOP 10. The most OP tank of all the times is 
of course the legendary `r md_link_tank(tank_names='Type 98 Ke-Ni Otsu', update=update_ver)`. 
It was released with wrong parameters and never sold since. WG did not 
dare to nerf it since some players managed to buy it before WG noticed 
the mistake. Due to its rarity (and age) it's not played much and thus 
it is not visible in the `r md_link_update()` on [BlitzAnalysiz[]](/).

```{r fig_top20_tanks_Relative_WR_all_time}
res <- head(stats[DT_filter_enough_battles.rWR(stats),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(all.battles),
    "Vehicle Class" = first(type),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)

plot_col_discrete_2Y(res, "Top 20 Tanks by Relative WR of all times", update,
  x_name, y_name, y2_name,
  fill_var = "Vehicle Class", y2_pct = FALSE
)
```


#### The most OP tanks of all times - Table

{{% expand "Show table" %}}
```{r top20_tanks_Relative_WR_all_time, echo = FALSE}
rm(stats)
md_table(res, update_ver = update)
```
{{% /expand %}}
