---
title: "Update 8.0 final stats added "
linktitle: "2021-07-17 Update 8.0 final stats added"
date: `r today("UTC")`
publishdate: 2021-07-17
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "8.0" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = "svglite", fig.ext = "svgz")
update_ver <- "8.0"
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles = sum(all.battles), Players = uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were 152M battles by 477k players recorded in the database during 
the `r md_link_update(update=update_ver)`.

* Not much changes in the best performing tanks:

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver)
```

### New American heavies

The American experimental heavy tank line leading to 
`r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` was introduced 
in `r md_link_update(update="8.0")`: 

####  Tier VII - M-III-Yoh

The `r md_link_tier(update=update_ver, tier=7)` 
`r md_link_tank(tank_names='M-VII-Yoh', update=update_ver)` felt a good tank, 
but it seems to have performed pretty poorly on average. 

```{r fig_tanks_tier7_heavy_RelativeWR}
tank_type <- "Heavy Tank"
tierN <- 7
stats <- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```


####  Tier VIII - M-III-Yoh

The `r md_link_tier(update=update_ver, tier=8)` `r md_link_tank(tank_names='M-III-Yoh', update=update_ver)` 
was introduced as a very balanced tank. In other words it is performing below-average for a heavy tank. 
I found the tank pretty decent. 

```{r fig_tanks_tier8_heavy_RelativeWR}
tank_type <- "Heavy Tank"
tierN <- 8
stats <- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

#### Tier IX - M-V-Yoh

The `r md_link_tier(update=update_ver, tier=9)` `r md_link_tank(tank_names='M-V-Yoh', update=update_ver)` 
was not so fun tank to play due to its enormous reload time. It performed bit below average. 

```{r fig_tanks_tier9_heavy_RelativeWR}
tank_type <- "Heavy Tank"
tierN <- 9
stats <- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

#### Tier X - M-VI-Yoh

The `r md_link_tier(update=update_ver, tier=10)` `r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` 
continues the pattern and performed below average. I liked the tank, but I have 
been fairing pretty poorly with it. I like the dual-shot gun more due to its 
unique characteristics, but the three-shot autoloader has far better DPM and 
seems to perform better. WG could give the dual-shot gun bit shorter magazine 
reload to make it more competitive. There is already 
`r md_link_tank(tank_names='T57 Heavy Tank', update=update_ver)` so playing the 
three-shot gun feels bit "meh" (IMO) - even it performs better.

```{r fig_tanks_tier10_heavy_RelativeWR}
tank_type <- "Heavy Tank"
tierN <- 10
stats <- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

If you have seen the `r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` 
performing well on the battlefield, it is probably since it has been driven by 
better than average players:

```{r fig_player_base_M_VI_Yoh}
tank_id <- get_tank_id("M-VI-Yoh")
tank_type <- get_tank_type(tank_id)
tank_types <- paste0(tank_type, "s")
tierN <- get_tank_tier(tank_id)
stats <- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_player_base(
    stats = stats, tank_id = tank_id,
    title.avg = paste("Tier", get_tier_roman(tierN), tank_types),
    update = update_ver
)
```
