---
title: "Update 7.8 final stats added "
linktitle: "2021-05-02 Update 7.8 final stats added"
date: `r today("UTC")`
publishdate: 2021-05-02
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.8" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.8'
stopifnot(all(exists("stats.update"), update_ver == update))
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 


* In total, there were 169M battles by 483k players recorded in the database 
during the `r md_link_update(update=update_ver)`.

* It is getting boring the report the best performing tanks - the same ones 
keep topping the charts update after update in slightly different order:  
1) `r md_link_tank(tank_names='T28 Concept', update=update_ver)`, 
2) `r md_link_tank(tank_names='Object 252U', update=update_ver)`, 
3) `r md_link_tank(tank_names='Annihilator', update=update_ver)`,  
4) `r md_link_tank(tank_names='T54E2', update=update_ver)` and 
5) `r md_link_tank(tank_names='Maus', update=update_ver)`.

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* `r md_link_update(update=update_ver)` was rather boring update without any major 
balance changes at the high tiers. `r md_link_tank(tank_names='121B', update=update_ver)` 
got buffed a bit and it improved a bit. But the best performing 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Medium Tank')`
stayed the same: 
1) `r md_link_tank(tank_names='T-22 medium', update=update_ver)`, 
2) `r md_link_tank(tank_names='Progetto M40 mod. 65', update=update_ver)` and 
3) `r md_link_tank(tank_names='E 50 Ausf. M', update=update_ver)`. 

```{r fig_tanks_tier10_MTs_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
																tank_type = tank_type, tier = tierN, topN = NULL)
``` 	

* Finally there is few updates since the Czechoslovakian medium tanks got introduced and 
it is now fair to say that the early assessment of those being _"meh"_ at the best was 
spot-on. The tanks (`r md_link_tank(tank_names='TVP T 50/51', update=update_ver)`,  
`r md_link_tank(tank_names='Škoda T 50', update=update_ver)`, etc.) were 
performing average across the player skill-levels. 

* The next new line seems to be experimental American heavies ending up to 
`r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` that is being 
super-tested at the moment by all-but-average players: 

```{r fig_tank_player_base_M_VI_Yoh}
tank_id     <- get_tank_id('M-VI-Yoh')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- get_stats.update.tier.type(DT = stats.update.perf, tierN = tierN, tank_type = tank_type)
plot_tank_player_base(stats = stats, tank_id = tank_id, 
                      title.avg = paste('Tier', get_tier_roman(tierN), tank_types), 
                      update = update_ver)
```

While the `r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` players are 
super unicums, the tank seems to perform extremely well for the super-testers even by 
their own standards. I am expecting WG to nerf the tank big time before releasing it. 

```{r fig_tank_relativeWR_M_VI_Yoh}
tank_id     <- get_tank_id('M-VI-Yoh')
tierN 			<- get_tank_tier(tank_id)
tank_type  	<- get_tank_type(tank_id)
stats 			<- get_stats.update.tier.type(DT = stats.update.perf, tierN = tierN, tank_type = tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```
