---
title: "R Notebook"
output: html_notebook
---



```{r}
stats.update <- load_tank_stats_update('7.5')
stats.update.tier8 <- subset(stats.update, (tier ==8) & (all.battles > 50))
stats.update.tier8 <- get_stats_tank_perf(stats.update.tier8)
players = stats.update.tier8[,.(Players=uniqueN(account_id))]
nrow(stats.update.tier8) / nrow(stats.update[tier==8])
```

```{r}
## List tanks by players
stats.update.tier8[,.(Players=.N), by=.(Tank=name)][order(-Players)]

# Tier VIII
model.tier8 <- lm(WR ~ DR + avg_dmg + avg_kills + spot_rate, weights = all.battles, data=stats.update.tier8[all.battles > 200] )

# T34
model.tier8.T34 <- lm(WR ~ DR + avg_dmg + avg_kills + spot_rate, weights = all.battles, data=stats.update.tier8.T34[all.battles > 200] )
```


```{r}
WR_mtrx      <- as.data.table(dcast(stats.update.tier8, 
                                                account_id ~ tank_id , 
                                                value.var = 'WR', fill=0))
btl_mtrx <- as.data.table(dcast(stats.update.tier8, 
                                                account_id ~ tank_id , 
                                                value.var = 'all.battles', fill=0))

## Does not work until I can map tank.perf to each row...
# Sparse matrix lm()?? 
#battles.t <- as.data.table(dcast(stats.update.tier8, account_id + tank_id ~ account_id , value.var = 'all.battles', fill=0))

account_ids <- WR_mtrx[, account_id]

WR_mtrx[, account_id:=NULL]
btl_mtrx[, account_id:=NULL]

tank_ids <- as.integer(colnames(WR_mtrx))
tank_names <- tanks[tank_id %in% tank_ids, .(tank_id, name)][match(tank_id, tank_ids)]$name

played_mtrx <- btl_mtrx
played_mtrx[played_mtrx > 0] <- 1

win_mtrx <- btl_mtrx * WR_mtrx

tank.wins <- colSums(win_mtrx)
player.wins <- rowSums(win_mtrx)

btl_mtrx <- btl_mtrx[rowSums(played_mtrx) > 1]
win_mtrx <- win_mtrx[rowSums(played_mtrx) > 1]
played_mtrx <- played_mtrx[rowSums(played_mtrx) > 1]

###
res <- est_tank_player_perf(btl_mtrx, win_mtrx, 50, verbose = TRUE)
names(res$tank.perf) <- tank_names
sort(res$tank.perf)
###


### 20+ battles
#> nrow(btl_mtrx)
#[1] 177673
# > sum(played_mtrx)
# [1] 681962
# > sum(btl_mtrx)/1e6
# [1] 69.24771

### 50+ battles
# > nrow(btl_mtrx)
# [1] 104289
# > sum(played_mtrx)
# [1] 333110
# > sum(btl_mtrx)/1e6
# [1] 54.32161

player.skill <- rep(1, nrow(btl_mtrx)) 

tank.perf <- rep(1, ncol(btl_mtrx))

tank.perf <- runif(ncol(btl_mtrx), 0.5, 1.5)

```



```{r tiers8_10}
stats.update.tier8_10 <- subset(stats.update, (tier >=8) & (all.battles > 50))
stats.update.tier8_10 <- get_stats_tank_perf(stats.update.tier8_10)

WR_mtrx      <- as.data.table(dcast(stats.update.tier8_10, 
                                                account_id ~ tank_id , 
                                                value.var = 'WR', fill=0))
btl_mtrx <- as.data.table(dcast(stats.update.tier8_10, 
                                                account_id ~ tank_id , 
                                                value.var = 'all.battles', fill=0))

## Does not work until I can map tank.perf to each row...
# Sparse matrix lm()?? 
#battles.t <- as.data.table(dcast(stats.update.tier8, account_id + tank_id ~ account_id , value.var = 'all.battles', fill=0))

account_ids <- WR_mtrx[, account_id]

WR_mtrx[, account_id:=NULL]
btl_mtrx[, account_id:=NULL]

tank_ids <- as.integer(colnames(WR_mtrx))

win_mtrx <- btl_mtrx * WR_mtrx

tank.wins <- colSums(win_mtrx)
player.wins <- rowSums(win_mtrx)

played_mtrx <- btl_mtrx
played_mtrx[played_mtrx > 0] <- 1

btl_mtrx <- btl_mtrx[rowSums(played_mtrx) > 1]
win_mtrx <- win_mtrx[rowSums(played_mtrx) > 1]
played_mtrx <- played_mtrx[rowSums(played_mtrx) > 1]

###
res <- est_tank_player_perf(btl_mtrx, win_mtrx, 50, verbose = TRUE)
###

tank_names <- tanks[tank_id %in% tank_ids, .(tank_id, name)][match(tank_id, tank_ids)]$name
names(res$tank.perf) <- tank_names
sort(res$tank.perf)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
