---
title: "Update 8.3 final stats added "
linktitle: "2021-10-24 Update 8.3 final stats added"
date: `r today("UTC")`
publishdate: 2021-10-24
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "8.3" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '8.3'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were `r auto_format(res$Battles)` battles by `r auto_format(res$Players)` 
players recorded in the database during the `r md_link_update(update=update_ver)`.

* The `r md_link(update=update_ver, link_text="TOP20 best performing tanks", rel_link="#highest-relative-wr")` 
list has undergone some big changes. 

* `r md_link_tank(tank_names='T110E3', update=update_ver)` that got a 
cupola-armor nerf in `r md_link_update(update="8.2")` has dropped to 
18th (was 13th in `r md_link_update(update="8.2")`.

* `r md_link_tank(tank_names='AT 15A', update=update_ver)` has taken 
the top position - maybe the armor highlighting change has helped it and 
other well-armored tanks? 

* `r md_link_tank(tank_names='Predator Ultramarines', update=update_ver)` 
is 4th after the usual `r md_link_tank(tank_names='T28 Concept', update=update_ver)` 
and `r md_link_tank(tank_names='Object 252U', update=update_ver)`. I have 
never played it, but I have always regarded is as an average tank. Maybe the 
armor-highlighting change in `r md_link_update(update="8.1")` boosted it a 
bit? Although, it seems to have performed above average (inline with 
`r md_link_tank(tank_names='Dracula', update=update_ver)`) in 
`r md_link_update(update="8.0")`.

* `r md_link_tank(tank_names='IS-7', update=update_ver)` has made 
into TOP 10 (8th) and is now clearly ahead of 
`r md_link_tank(tank_names='IS-4', update=update_ver)`. Recommended. 

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver)
```

`r md_link_tank(tank_names='Annihilator', update=update_ver)` is still making  
`r md_link(update=update_ver, link_text="40% above tier VII average damage", rel_link="#highest-average-damage-tier-for-tier")` 
 even it is not winning anymore. [Rigged MM](/blog/2021-08-22_8.1_final_stats_added/#annihilators-nerf) is a bitch. 

```{r fig_tanks_all_avg_dmg_highest}
plot_avg_dmg_tier4tier(stats = stats.update.perf, update = update_ver)
```
