---
title: "1 Million players"
linktitle: "2021-02-27 1 Million players"
date: `r today("UTC")`
publishdate: 2021-02-27
author: Jylpah@gmail.com
disableToc: false
output: md_document
weight: page_weight
alwaysopen: false
hidden: true
tags: [ "post", "7.6" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = c("svglite", "png"))
# Load stats
update_ver <- "7.6"
NOW <- as.integer(as.POSIXct("2021-02-25")) # 7.6 Stats fetched on Feb 24, 2021

# Get last_battle_time & all.battles per tank per account

res <- qread(filename_data("summary_tank_stats_0.9-7.6.qs"))

stats <- res[, head(.SD, 1), by = .(account_id, tank_id)]
first_battle_times <- res[, .(first_battle_time = min(last_battle_time)),
  by = .(account_id, tank_id)
]

rm(res)
gc(verbose = FALSE)

setkey(stats, account_id, tank_id)
setkey(first_battle_times, account_id, tank_id)

stats <- merge(stats, first_battle_times,
  by = c("account_id", "tank_id"), all.x = TRUE
)
stats[, WR := all.wins / all.battles]
stats[, WR.career := sum(all.wins) / sum(all.battles), by = account_id]

stats <- na.omit(stats)

accounts <- stats[, .(
  WR.career = first(WR.career), battles = sum(all.battles),
  tanks = .N, career_time = max(last_battle_time) - min(first_battle_time),
  last_battle_time = max(last_battle_time),
  first_battle_time = min(first_battle_time)
),
by = account_id
]
```

BlitzAnalysiz[] recently reach an impressive milestone: the site's database tracks 
now over **1 million players**! That's is a big number so let's have a look on 
the player base. 

## Career WR

The chart below shows player's career WR over those 1M players. The career WR distribution seems 
*almost* normal distribution, but only almost. The right-hand side "tail" is reaching further 
from the mean vs. the left-hand side and the mean WR is above 50%. This seems impossible. 
This is likely related to the sampling of the players, since more active players 
are more likely to end up in the the database. Many players (38%) have given up the 
game or at least have not played in 2021. It seems the the success of the player 
does not influence on the decision to give up on the game - at least among those 
who have ended into the database.    

```{r fig_career_wr}
cut_off <- as.integer(as.POSIXct("2021-01-01"))

res <- stats[, .(
  "WR" = first(WR.career),
  "Player" = factor(max(last_battle_time) > cut_off,
    levels = c(TRUE, FALSE), labels = c("Active", "Inactive")
  )
),
by = account_id
]

plot_histogram_continuous(res, "Career WR", NULL, "WR", "Players",
  fill_var = "Player", fill_elems = c("Active", "Inactive"),
  avg_name = "Total",
  y_pct = TRUE, x_pct = TRUE, bin_breaks = seq(.2, .8, .01),
  x_lims = c(.2, .8), x_breaks = seq(.2, .8, .05),
  x_signif = 3,
  stacked = TRUE, median = FALSE,
  palette.fill = palette.graphs[c(7, 8)],
  palette.annotate = palette.lines[c(7, 8)]
)
```

### Career WR table

This table shows the career WR of the players as [quantiles](https://en.wikipedia.org/wiki/Quantile). 

{{% expand "Show table" %}}

```{r career_battle_count_summary, echo = FALSE}
md_table_quantiles(res[, WR], "WR", c(seq(0, 0.04, 0.01), seq(0.05, 0.9, .05), seq(0.95, 1, .01)))
```

{{% /expand %}}

## Length of the Blitz Career

The next chart looks how long the players have been playing Blitz so far. The mean 
is 2.7 years and the chart is surprisingly flat. 

```{r fig_career_length}
plot_histogram_continuous(accounts[, .(Years = career_time / 3600 / 24 / 365)],
  "Blitz Career length", NULL, "Years", "Players",
  y_pct = TRUE, x_pct = FALSE, bins = 70, x_breaks = seq(0, 7)
)
```

## Career start 

The following chart shows when did the players start playing Blitz. 
**However**, this does not give true picture since the database has 
been collected only since update 5.3 (2018 September). I do have earlier 
data sets, but I have not had time to integrate those in the main database 
for the enjoyment for those handful hard-core Blitz stats nerds. Some day 
I will. Also strictly speaking it shows the oldest last battle time across the 
players' tanks. The chart therefore tells how long the players have at least played. 

```{r fig_career_start}
bin_breaks <- as.integer(as.POSIXct(seq(as.Date("2014-01-01"), by = "month", length.out = 9 * 12)))
x_labels <- seq(as.Date("2014-01-01"), by = "year", length.out = 9)
x_breaks <- as.integer(as.POSIXct(x_labels))
x_labels <- year(x_labels)
plot_histogram_continuous(accounts[, .("Year" = first_battle_time)],
  "Players by start of their Blitz Career", NULL, "Year", "Players",
  y_pct = TRUE, x_pct = FALSE, bin_breaks = bin_breaks, x_breaks = x_breaks,
  x_labels = x_labels, mean = FALSE, median = FALSE
)
```

## Latest battle

The chart shows when did the players tracked by the site play the last time. Only 
50% of the tracked players have played in current month (Feb 2021). The slope of the 
chart does not indicate the the exodus from the game increasing since also the site 
has constantly increased the number of players being tracked. But it shows that there 
is a large player base who do not play Blitz even every month. 

```{r fig_career_end}
bin_breaks <- as.integer(as.POSIXct(seq(as.Date("2018-01-01"), by = "month", length.out = 9 * 12)))
x_labels <- seq(as.Date("2018-01-01"), by = "year", length.out = 9)
x_breaks <- as.integer(as.POSIXct(x_labels))
x_labels <- year(x_labels)
plot_histogram_continuous(accounts[, .("Year" = last_battle_time)],
  "Players by their latest battle", NULL, "Year", "Players",
  y_pct = TRUE, x_pct = FALSE, bin_breaks = bin_breaks, x_breaks = x_breaks,
  x_labels = x_labels, mean = FALSE, median = FALSE
)
```