---
title: "Update 7.6 final stats added "
linktitle: "2021-02-27 Update 7.6 final stats added"
date: `r today("UTC")`
publishdate: 2021-02-27
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.6"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.6'
stopifnot(all(exists("stats.update"), update_ver == update))
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* `r md_link_update(update=update_ver)` marked a great milestone for the site. BlitzAnalysiz[] 
is now tracking the performance of more than [**1 million players**](/blog/2021-02-27_1m_accounts/)! 

* In total, there were 328M battles by 515k players recorded in the database during 
the `r md_link_update(update=update_ver)`. 

```{r fig_tanks_top_averageWR}
plot_averageWR(stats = stats.update.perf, update = update_ver);
```

* `r md_link_tank(tank_names='T28 Concept', update=update_ver)` retook the #1 spot 
after `r md_link_tank(tank_names='T54E2', update=update_ver)` and 
`r md_link_tank(tank_names='AT 15A', update=update_ver)`. There are not any Tech Tree 
tanks in TOP 5 and only two in TOP 10.  

```{r fig_tanks_top_relativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```
