---
title: "Vehicle Class (Im)Balance"
linktitle: "2021-03-13 Vehicle Class (Im)Balance"
date: `r today("UTC")`
publishdate: 2021-03-13
author: Jylpah@gmail.com
disableToc: false
output: md_document
weight: page_weight
alwaysopen: false
hidden: true
tags: [ "post", "7.6" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = "svglite", fig.ext = "svgz")
update_ver <- "7.6"
min_players.pct <- 0.005
```

I my view, the game became more boring after WG added *Vehicle Class Matching* rules into the 
MatchMaker (update 5.1). The exact vehicle class matching rules have been adjusted since, 
but basically the Vehicle Class Matching  limits the number of Tank Destroyers and Light 
Tanks per team and makes sure there is only +/-1 tank difference between the teams across 
the vehicle classes. This results mirrored teams causing monotonic battles. In my view, 
most of the vehicle class matching rules should be abolished, but I know well how I am 
in the minority here. 

```{r fig_tanks_all_Relative_WR_topN}
stats.update.tiers <- subset(stats.update, tier >= 5)
stats.update.tiers <- get_stats_tank_perf(stats.update.tiers)
Nplayers <- stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers), uniqueN(account_id)]
res <- head(stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers),
  .(
    "Relative WR" = mean(rWR),
    "Players" = uniqueN(account_id),
    "Vehicle Class" = first(type)
  ),
  by = name
][Players >= Nplayers * min_players.pct][order(-`Relative WR`)], n = 20)
x_name <- "Tank"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Top 20 Tanks by Relative WR", "All players Tiers V-X")
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```

But the MM is not the main story of this post, but a long intro to the issue at 
hand - **the imbalance of the vehicle classes in the game**. I believe WG tried 
to solve fundamentally a balancing issue through the Vehicle Class Matching -rules. 
And while there is a logic in their thinking, they could have fixed the root cause 
instead and do better job balancing the tanks. When looking at the  best performing 
tanks chart above, you can notice how light tanks are completely missing from the 
list and how the mediums are severely under presented. **Heavies and heavily armored TDs rule**. 

# Performance Vehicle Classes

The average performance of vehicle classes varies per tier and per player skill class. 
But there are certain patterns I am going to show below. I have used the 
`r md_link_update(update=update_ver)` data since that is the latest update 
with full stats available at the moment. 

{{% expand "Techical details" %}}
* The calculation of the average Relative WR of a vehicle class has been done *without* weighting 
the data with the number of players. This avoids bias caused by hugely popular tanks like 
`r md_link_tank(tank_names='FV215b (183)', tank_str = 'Death Star', update=update_ver)`). 
* In practice this means calculating Relative WR for each tank first and then taken 
averages per vehicle class. 
* This eliminates the bias caused by popular tanks and each tank's relative WR has 
the same weight regardless of the number of players playing it. 
* However, the tanks played by less than 0.5% of the (tier's) player base have been 
excluded from the vehicle class averages completely.  
{{% /expand %}}

# Tier X
```{r}
tierN <- 10
```

Let's first look at the `r md_link_tier(update=update_ver, tier=10)`. 

## All players

While the absolute differences are not massive, it is clear that the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)` 
out-perform all the other vehicle classes when looking the stats over all the players. 
The `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` perform 
the worst as one would expect due to the 
[_high skill-floor_](https://esportsedition.com/general/skill-ceiling-skill-floor-esports-terminology/) 
of those. The heavies on the other hand are often well-armored and more forgiving to drive.

```{r fig_vehicle_classes_tier10_Relative_WR}
tierN <- 10
stats.tier <- get_stats.update.tier(tierN)
stats.tier <- get_stats_tank_perf(stats.tier)
Nplayers <- stats.tier[DT_filter_enough_battles.rWR(stats.tier), uniqueN(account_id)]

res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", paste("Tier", get_tier_roman(tierN), "All players"))
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

Let's now look the performance in different player skill categories.

## Players with < 45% WR at Tier X

```{r fig_vehicle_classes_tier10_Relative_WR_sub45}
WR.min <- 0
WR.max <- .45

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```

_N = `r Nplayers`_

As expected, the less-skilled players struggle a lot with the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)`
 and do the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` 
best with the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` 
that allow them to keep distance to the front line. But the stats of the low-skilled 
players cannot be used for balancing the tanks and vehicle classes.

## Players with 45-55% WR at Tier X

```{r fig_vehicle_classes_tier10_Relative_WR_45_55}
WR.min <- .45
WR.max <- .55

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

For an average tier X player, the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)`
perform the best and the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` 
clearly the worst. The `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` are 
almost perfectly balanced (on average). This is very much the expected result. 


## Players with 55-65% WR at Tier X

```{r fig_vehicle_classes_tier10_Relative_WR_55_65}
WR.min <- .55
WR.max <- .65

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

Wargaming has communicated it bases its balancing decisions 
(commercial motivations set aside) to the performance of the "players with 55-65% WR". 
What exacly does the "players with 55-65% WR" mean is not completely clear, but 
this player segment should be close to Wargaming's "vehicle balancing focus group".  

For the 55-65% WR players, the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)` 
perform even better than for the average players. The 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Medium Tank', plural=TRUE)` have 
improved too and are now _perfectly_ balanced. The 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` 
have dropped to the 3rd spot and the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)`
continue to drag behind the rest. Clearly the skill-floor of the light tanks is still too high 
for this player category. 

## Players with 65%+ WR at Tier X

```{r fig_vehicle_classes_tier10_Relative_WR_65plus}
WR.min <- .65
WR.max <- 1

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

When looking at the very good players (WR 65%+ at tier X), the picture is again 
bit different. The 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` 
perform clearly better are now very well balanced along with the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Medium Tank', plural=TRUE)`. 
The `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)`
still perform the best and the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` 
have dropped to the last underperform significantly (on average). There are exceptions 
though like `r md_link_tank(tank_names='T110E3', update=update_ver)` 
and `r md_link_tank(tank_names='AMX 50 Foch (155)', update=update_ver)`. 

## Players with 75%+ WR at Tier X
```{r}
Nplayers <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
  (WR.tier.maxed > .75), uniqueN(account_id)]
Nbattles <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
  (WR.tier.maxed > .75), sum(all.battles)]
```

I also checked how the _Ultra-Super-Unicums_ (players with 75%+ WR at the tier X) perform. 
First of all, there are not that many of them (only `r Nplayers` in the database), 
but that is still a solid number and there is a solid number of battles (`r Nbattles`) 
behind the numbers. 

```{r fig_vehicle_classes_tier10_Relative_WR_75plus}
WR.min <- .75
WR.max <- 1

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The gaps between the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)` 
and the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Medium Tank', plural=TRUE)` and 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` 
have now shrunk to irrelevant. But the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` 
perform significantly worse. The -3% relative WR difference is at the same level as the 
difference between `r md_link_tank(tank_names='Annihilator', update=update_ver)` 
and `r md_link_tank(tank_names='Challenger', update=update_ver)`.

## Tier X Conclusion

It is clear that the `r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Heavy Tank', plural=TRUE)` 
outperform all the tank-classes and the 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Tank Destroyer', plural=TRUE)` 
underperform (on average). The 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Medium Tank', plural=TRUE)` and 
`r md_link_tier_tank_type(update=update_ver, tier=10, tank_type = 'Light Tank', plural=TRUE)` 
seem balanced although the light tanks have very high skill-floor. Naturally the tank balancing 
has to be done tank by tank and WG should treat e.g. 
`r md_link_tank(tank_names='T110E3', update=update_ver)` and 
`r md_link_tank(tank_names='Grille 15', update=update_ver)` differently. 

# Tier IX

## All players

```{r fig_vehicle_classes_tier9_Relative_WR}
tierN <- 9
stats.tier <- get_stats.update.tier(tierN)
stats.tier <- get_stats_tank_perf(stats.tier)

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier),
  uniqueN(account_id)
]

res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", paste("Tier", get_tier_roman(tierN), "All players"))
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The vehicle classes' average performance at `r md_link_tier(update=update_ver, tier=9)` is bit different than what could 
be expected. Seeing the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Light Tank', plural=TRUE)` 
to out-perform the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)` 
among all the players is odd. More about that below. 

## Players with < 45% WR at tier IX

```{r fig_vehicle_classes_tier9_Relative_WR_sub45}
WR.min <- 0
WR.max <- .45

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The results for the less-skilled players (tier IX WR < 45%) are quite as expected, except that the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Light Tank', plural=TRUE)`
 out-perform the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)`. 
This is an indication that the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Light Tank', plural=TRUE)` 
are very strong compared to the `r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank')` counterparts. The 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Light Tank', plural=TRUE)`
should have a high skill-floor.

## Players with 45-55% WR at tier IX

```{r fig_vehicle_classes_tier9_Relative_WR_45_55}
WR.min <- .45
WR.max <- .55

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

For the average players (45-55% WR at tier IX), the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Heavy Tank', plural=TRUE)` 
outperform the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Tank Destroyer', plural=TRUE)`
and the `r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Heavy Tank', plural=TRUE)`
drag behind others. 

## Players with 55-65% WR at tier IX

```{r fig_vehicle_classes_tier9_Relative_WR_55_65}
WR.min <- .55
WR.max <- .65

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The WG's "vehicle balancing focus group" clearly reveals how the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)`
underperform. This player category should be able to leverage the better mobility of the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)`,
but those still perform the worst with a margin . 


## Players with 65%+ WR at tier IX

```{r fig_vehicle_classes_tier9_Relative_WR_65plus}
WR.min <- .65
WR.max <- 1

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The vehicle class performance in the hands of very good players (Tier IX WR 65%+) 
clearly show the imbalances at 
`r md_link_tier(update=update_ver, tier=9)`. The 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Light Tank', plural=TRUE)` 
are  outperforming the rest and even the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Tank Destroyer', plural=TRUE)`
are outperforming the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)`. 
The poor performance of the 
`r md_link_tier_tank_type(update=update_ver, tier=9, tank_type = 'Medium Tank', plural=TRUE)`
in the hands of the most skilled players shows how the tier's medium tanks need some buffs. 
However, the absolute differences are not massive: less than 1% between the best and worst 
performing vehicle class. **The Tier IX is probably the most balanced tier in the game at the moment**. 

# Tier VIII

`r md_link_tier(update=update_ver, tier=8)` is the most popular tier in the game. 

## All players

```{r fig_vehicle_classes_tier8_Relative_WR}
tierN <- 8
stats.tier <- get_stats.update.tier(tierN)
stats.tier <- get_stats_tank_perf(stats.tier)


Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier),
  uniqueN(account_id)
]

res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", paste("Tier", get_tier_roman(tierN), "All players"))
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

At `r md_link_tier(update=update_ver, tier=8)`, the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Heavy Tank', plural=TRUE)` 
perform the best and the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Tank Destroyer', plural=TRUE)` and 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Medium Tank', plural=TRUE)` 
share the 2nd place. The 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Light Tank', plural=TRUE)` 
underperform the other vehicle classes (as they should for all the players).

## Players with < 45% WR at Tier VIII

```{r fig_vehicle_classes_tier8_Relative_WR_sub45}
WR.min <- 0
WR.max <- .45

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The `r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Heavy Tank', plural=TRUE)` 
perform the best in the hands of less-skilled players, and the order of vehicle 
classes is very much in line with the expectations. 

## Players with 45-55% WR at Tier VIII

```{r fig_vehicle_classes_tier8_Relative_WR_45_55}
WR.min <- .45
WR.max <- .55

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The order stays the same for the average players. No surprises here. 

## Players with 55-65% WR at Tier VIII

```{r fig_vehicle_classes_tier8_Relative_WR_55_65}
WR.min <- .55
WR.max <- .65

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

For the 55-65% player segment the situation changes a bit and the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Medium Tank', plural=TRUE)` 
take the 2nd place. The poor performance of the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Light Tank', plural=TRUE)` 
in the hands of good players is not normal but a sign of severe underperformance of the tier VIII LTs. The 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Heavy Tank', plural=TRUE)`
lead is so expected that it is easy take it for granted even though it would not have to be so. 

## Players with 65%+ WR at Tier VIII

```{r fig_vehicle_classes_tier8_Relative_WR_65plus}
WR.min <- .65
WR.max <- 1

Nplayers <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  uniqueN(account_id)
]

res <- stats.tier[
  DT_filter_enough_battles.rWR(stats.tier) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .("Relative WR" = mean(rWR), "Vehicle Class" = first(type), Players = .N),
  by = .("Tank" = name)
][Players > Nplayers * min_players.pct,
  .("Relative WR" = mean(`Relative WR`)),
  by = `Vehicle Class`
]

# res <- stats.tier[DT_filter_enough_battles.rWR(stats.tier) &
#                            (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
#                          .('Relative WR'  = mean(rWR)), by=.('Vehicle Class'= type) ]

x_name <- "Vehicle Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle(
  "Relative WR by Vehicle Class",
  paste(
    "Tier", get_tier_roman(tierN), "Player WR",
    percent_range_format(c(WR.min, WR.max))
  )
)
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

The `r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Heavy Tank', plural=TRUE)` 
continue to rule and the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Light Tank', plural=TRUE)`
continue to struggle even in the hands of very good players. This is a clear sign of the 
underperformance of the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Light Tank', plural=TRUE)`. 

# Tiers V-X

Let's now look the situation across tiers V-X. The graph below plots the performance of 
vehicle classes per tier. I am plotting the charts for all the players, 
and WR 55-65% and WR 65%+ player categories. 

## All players

```{r fig_vehicle_classes_tiers6_10_Relative_WR}
Nplayers <- stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers), uniqueN(account_id)]
res <- stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers),
  .(
    "Relative WR" = mean(rWR),
    "Players" = uniqueN(account_id),
    "Vehicle Class" = first(type),
    "Tier" = first(tier)
  ),
  by = name
][Players >= Nplayers * min_players.pct]

res <- res[, .("Relative WR" = mean(`Relative WR`)), by = .(Tier, `Vehicle Class`)][order(-`Relative WR`)]

res[, "Tier - Class" := paste("Tier", get_tier_roman(Tier), `Vehicle Class`)]

x_name <- "Tier - Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", "Tiers V-X All players")
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

## Players with 55-65% WR

```{r fig_vehicle_classes_tiers6_10_Relative_WR_55_65}
WR.min <- .55
WR.max <- .65

Nplayers <- stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers) &
  (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max), uniqueN(account_id)]
res <- stats.update.tiers[
  DT_filter_enough_battles.rWR(stats.update.tiers) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .(
    "Relative WR" = mean(rWR),
    "Players" = uniqueN(account_id),
    "Vehicle Class" = first(type),
    "Tier" = first(tier)
  ),
  by = name
][Players >= Nplayers * min_players.pct]

res <- res[, .("Relative WR" = mean(`Relative WR`)), by = .(Tier, `Vehicle Class`)][order(-`Relative WR`)]

res[, "Tier - Class" := paste("Tier", get_tier_roman(Tier), `Vehicle Class`)]

x_name <- "Tier - Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", paste(
  "Tiers V-X Player WR",
  percent_range_format(c(WR.min, WR.max))
))

plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

## Players with 65%+ WR

```{r fig_vehicle_classes_tiers6_10_Relative_WR_65plus}
WR.min <- .65
WR.max <- 1

Nplayers <- stats.update.tiers[DT_filter_enough_battles.rWR(stats.update.tiers) &
  (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max), uniqueN(account_id)]
res <- stats.update.tiers[
  DT_filter_enough_battles.rWR(stats.update.tiers) &
    (WR.tier.maxed > WR.min) & (WR.tier.maxed <= WR.max),
  .(
    "Relative WR" = mean(rWR),
    "Players" = uniqueN(account_id),
    "Vehicle Class" = first(type),
    "Tier" = first(tier)
  ),
  by = name
][Players >= Nplayers * min_players.pct]

res <- res[, .("Relative WR" = mean(`Relative WR`)), by = .(Tier, `Vehicle Class`)][order(-`Relative WR`)]

res[, "Tier - Class" := paste("Tier", get_tier_roman(Tier), `Vehicle Class`)]

x_name <- "Tier - Class"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_subtitle("Relative WR by Vehicle Class", paste(
  "Tiers V-X Player WR",
  percent_range_format(c(WR.min, WR.max))
))
plot_col_discrete_1Y(res, title, update_ver, x_name, y_name,
  y_pct = TRUE,
  palette.fill = palette.vehicle_class, fill_var = "Vehicle Class"
)
```
_N = `r Nplayers`_

## Conclusions

It should evident from the charts above how the 
**heavy tanks overperform** in the game, and how the 
**tank destroyers and light tanks underperform** with Tier IX light tanks 
being a notable exception. The  differences between the ends of the spectrum are sizable.

# How to re-balance the game again?

*It is easier to point out issues than fix those*. And while each 
tier (and tank) have to be balanced separately, the main re-balancing directions are clear:
* **The heavy tanks deserve nerfs** across the tiers with tier IX being an exception. 
* **The light tanks deserve buffs** with tier IX being an exception
* **The tank destroyers deserve buffs** across the tiers

The difficult part really is *how* to re-balance. 

I personally think nerfing the **heavy tanks'** traverse and turret traverse speeds 
should be the main ways to achieve  the balancing objectives. I think the WG's idea 
of increasing the heavy tanks' HP pools was a good one and inline with the role of 
the heavy tanks. Slightly reducing the mobility of the heavy tanks would enforce 
the differences between medium and heavy tanks and suit their respective roles. 

For the **tank destroyers**, I would probably buff camo while stationary and DPM. 
Buffing TDs, especially the campy, big alpha ones is a controversial topic since 
many TDs are already hugely popular despite their poor performance. Players just 
love the big-alpha tanks for the occasional giggles. Buffing those could  change 
the meta towards more "campy" direction. And this is where the MM's *vehicle class 
matching* rules can come handy. Limiting the number of TDs entering the battles 
would increase the queuing times for those while keeping the battles clean from 
negative camping-effect of the TDs. This is the only vehicle class matching rule 
I personally support. Probably three TDs per team sounds like the right limit - 
unless it becomes a norm. 

Buffing the **light tanks** is harder. Some of the light tanks deserve engine 
buffs for better acceleration. Also improved view range could improve the performance
 while supporting the unique role of the light tanks.

Having said all this, I am certain WG's balancing department has far more 
competence on this area. They know what they are doing even though commercial 
motives sometimes overrule their balancing rulebook 
(`r md_link_tank(tank_names='Annihilator', update=update_ver)`, 
`r md_link_tank(tank_names='Smasher', update=update_ver)`, 
`r md_link_tank(tank_names='Gravedigger', update=update_ver)`, etc.). 
The good news is that the Grille line tank destroyers are about to receive 
buffs in update 7.8 in the form of new consumables (especially *Spall Liner*). 
So I believe WG is clearly aware of the current imbalances.

I hope you enjoyed this longer-than-intended read. Happy tanking and stay safe! 
