---
title: "Update 7.7 final stats added "
linktitle: "2021-03-26 Update 7.7 final stats added"
date: `r today("UTC")`
publishdate: 2021-03-26
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.7" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.7'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were 236M battles by 481k players recorded in the database 
during the `r md_link_update(update=update_ver)`.

* Familiar & well-armored tanks took the top spots in tank performance 
rankings: 1) `r md_link_tank(tank_names='Object 252U', update=update_ver)`, 
2) `r md_link_tank(tank_names='Annihilator', update=update_ver)` and 
3) `r md_link_tank(tank_names='T54E1', update=update_ver)`. There was only 
one Tech-Tree tank in the TOP 5 (`r md_link_tank(tank_names='Maus', update=update_ver)`) 
and two in TOP 10 (`r md_link_tank(tank_names='AT 8', update=update_ver)`).

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* `r md_link_tier(update=update_ver, tier=10)` performance ranking was 
the same armor-spam: 1) `r md_link_tank(tank_names='Maus', update=update_ver)`, 2)
`r md_link_tank(tank_names='IS-4', update=update_ver)`, 
3) `r md_link_tank(tank_names='E 100', update=update_ver)` 
and so on. All the TOP 10 tanks have a strong armor profile. What is interesting 
is that the order is pretty much the same for better-than-average players (55%+ WR at tier X). 

```{r fig_tanks_top20_tier10_RelativeWR}
tank_type  	<- NULL
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
																tank_type = tank_type, tier = tierN)
```

## Czechoslovakian medium tanks

So how did the Czechoslovakian tanks do? Short answer is: *"pretty bad"*, but in 
reality it is still too early to say. The Relative WR of the Czechoslovakian tanks 
will likely to improve in the next update as players learn to play the tanks better 
and a larger share of the player population has finished the *stock-grind*. 
Blitzanalysiz[] tries to eliminate the impact of the stock-grind by requiring 
players to have a tier-specific number of battles in a tank before their stats 
can be included into the calculations, but that seems not to fully eliminate 
the impact of the "stock-grind".

### Tier X TVP T 50/51

The `r md_link_tier(update=update_ver, tier=10)` 
`r md_link_tank(tank_names='TVP T 50/51', update=update_ver)` performed 
pretty average being among the lowest 1/3rd. It may have an unique playstyle, 
but it seem not to perform that well. 

```{r fig_tanks_tier10_mt_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN, topN=NULL)
```

If you constantly see `r md_link_tank(tank_names='TVP T 50/51', update=update_ver)`s 
to perform superb on the battlefield, that is simply because it has been played 
by very-very good players on average at this point. The rest of the players will 
grind it soon and the true (non-)performance of the tier X TVP will become more 
apparent. 

```{r fig_player_base_TVP5051}
tank_id     <- get_tank_id('TVP T 50/51')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_player_base(stats = stats, tank_id = tank_id, 
                      title.avg = paste('Tier', get_tier_roman(tierN), tank_types), 
                      update = update_ver)
```

### Tier IX Škoda T 50

The `r md_link_tier(update=update_ver, tier=9)` 
`r md_link_tank(tank_names='Škoda T 50', update=update_ver)` 
performed bit better, but it still just average. 

```{r fig_tanks_tier9_mt_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 9
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN, topN=NULL)
```

### Tier VIII TVP VTU Koncept

The `r md_link_tier(update=update_ver, tier=8)` 
`r md_link_tank(tank_names='TVP VTU Koncept', update=update_ver)` 
was a big disappointment to play. Based on stats it was the second worst 
performing tier VIII medium and the worst performing tier VIII medium 
for players with 55%+ WR at tier VIII.

```{r fig_tanks_tier8_mt_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 8
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN, topN=NULL)
```


### Tier VII Konštrukta T-34/100

I personally felt the `r md_link_tier(update=update_ver, tier=7)` 
`r md_link_tank(tank_names='Konštrukta T-34/100', update=update_ver)` 
was pretty decent, but based on stats it was actually one of the worst 
performing tier VII mediums.  

```{r fig_tanks_tier7_mt_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 7
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN, topN=NULL)
```


### Tier VI Škoda T 25

The `r md_link_tier(update=update_ver, tier=6)` 
`r md_link_tank(tank_names='Škoda T 25', update=update_ver)` 
fits the pattern and was one of the worst performing tier VI medium tanks. 

```{r fig_tanks_tier6_mt_RelativeWR}
tank_type  	<- 'Medium Tank'
tierN 			<- 6
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
                                tank_type = tank_type, tier = tierN, topN=NULL)
```

I still cannot believe the Czechoslovakian tanks were so bad. I think the 
"stock-grind" effect is there still.I dislike the tanks, but I  believe  
their stats will fair bit better (i.e. average) in update 7.8. Let's see. 

