```{r setup, include=FALSE}
knitr::opts_chunk$set(
    fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, error = FALSE,
    dev = "svglite", fig.ext = "svgz"
)
# Checks
stopifnot(exists("target_page"))
# stopifnot(exists('stats.career '))
update <- get_path_elem(target_page, 2)
cols.sel <- c(
    "account_id", "tank_id", "name", "tier", "is_premium", "wins",
    "battles", "battles.career", "wins.career", "battles.career.all",
    "WR.career.all"
)
if (exists("stats.career")) rm(stats.career)
stats.career <- ds_load_ts_career(update, cols = cols.sel)
tanks.enough_players <- get_tanks_enough_players(stats.career)
preliminary <- is_preliminary(update) # not used atm
var2rm <- c("res", "stats.career")
```
---
title: "Career stats" 
menutitle: "Career stats"
linktitle: "Career stats (`r update_version(update)`)"
date: `r today("UTC")`
author: Jylpah@gmail.com
output: md_document
weight: 3
description: "Analysis of Player career stats in World of Tanks Blitz mobile tank game. Update `r update`"
tags: [ "`r update`", "Career stats"  ]
disableToc: false
---

`r update_if_final(update, '', '_Preliminary stats_')`

```{r career_info, echo = FALSE}
res <- stats.career[, .(Battles = first(battles.career.all)),
    by = account_id
]
players <- nrow(res)
```

This page shows statistics of players' battles fought during their Blitz "career" until the end of **update `r update`**. 
In total, `r auto_format(players)` players played during update `r update`.

## Battles per Player

Number of career/cumulative battles per player in the end of the update `r update`.

```{r fig_career_battle_count_histogram}
plot_histogram(res, "Career Battles per Players", update,
    "Battles", "Share of Players %",
    x_lims = c(0, 100e3), x_step = 5000, y_step = 2.5 / 100, x_signif = 2,
    y_pct = TRUE, y_signif = 2
)

res <- res[, .(mean = mean(Battles), median = median(Battles), max = max(Battles))]
```

An average player has played `r as.integer(res$mean)` battles by the end of update `r update`. 
Median battle count was `r res$median` and the largest number of battles recorded by a single 
player (in the dataset) was `r auto_format(res$max)` battles. The following tables shows battle 
counts by N% most inactive players during the update (i.e. "90% most inactive" == "10% most active"). 

### Battles per Player table

{{% expand "Show table" %}}

The table below shows the (max) number of battles played until the end of `r update` by the 
X% most _inactive_ players. Reading tip: 10% most _active_ players have played more than the 
90% most _inactive_ players.

```{r career_battle_count_summary, echo = FALSE}
md_table_quantiles(stats.career[, .(Battles = first(battles.career.all)),
    by = account_id
][, Battles], "Battles", c(seq(0, .9, .05), seq(.91, 1, 0.01)))
```
{{% /expand %}}

## Player WR distribution

The following graph shows a histogram of players (y-axis) based on their career WR (x-axis). 
Only players with `r min_battles.career` battles or more are included.

```{r fig_career_player_WR_histogram}
res <- stats.career[battles.career.all >= min_battles.career,
    .(WR = first(WR.career.all)),
    by = account_id
]
plot_histogram(res, "Player Career WR distribution", update,
    x_name = "WR", y_name = "Share of Players",
    x_lims = c(.2, .8), x_step = .05, x_pct = TRUE,
    y_pct = TRUE, y_step = .01, binwidth = .01
)
```

{{% expand "Show table" %}}
```{r career_player_WR, echo = FALSE}
h <- hist(stats.career[,
    .(WR = first(WR.career.all)),
    by = account_id
][, WR], breaks = 100, plot = FALSE)
sum.counts <- sum(h$counts)
h$density <- h$counts / sum.counts
h$cum <- cumsum(h$density)
len <- length(h$breaks)
res <- data.table(
    "Career WR" = h$breaks[2:len],
    "Share %" = h$density,
    "Cumulative share %" = h$cum
)[(`Career WR` >= .2) & (`Career WR` < .81)]
md_table(res)
```
{{% /expand %}}

## Current WR vs. Career Battles played

This graph shows Player WR during the update `r update` vs. player career battles. Average tier is not taken into account.

```{r fig_career_battles_vs_current_WR, message=FALSE}
x_name <- "Battles"
y_name <- "WR"
fill_name <- "WR"
title <- "Current WR by Career Battles"

res <- stats.career[, .(
    "WR" = sum(wins) / sum(battles),
    "Battles" = first(battles.career.all)
),
by = account_id
][, .N, by = .(
    Battles = cut(Battles, breaks = buckets.battles.career, include.lowest = TRUE),
    WR = cut(WR, breaks = buckets.WR, include.lowest = TRUE)
)][order(Battles, WR)]

x_labels <- auto_range_format(buckets.battles.career)
fill_labels <- percent_range_format(buckets.WR)

plot_marimekko(res, title, update,
    x_name = "Battles", fill_var = "WR", palette.fill = palette.WN8,
    x_labels = x_labels, fill_labels = fill_labels
)
```

## Career WR vs. Career Battles played

This graph shows Player career WR vs. career battles. Average tier is not taken into account.

```{r fig_career_battles_vs_WR, message=FALSE}
x_name <- "Battles"
y_name <- "WR"
fill_name <- "WR"
title <- "Career WR by Career Battles"

res <- stats.career[, .(
    "WR" = first(WR.career.all),
    "Battles" = first(battles.career.all)
),
by = account_id
][, .N, by = .(
    Battles = cut(Battles, breaks = buckets.battles.career, include.lowest = TRUE),
    WR = cut(WR, breaks = buckets.WR, include.lowest = TRUE)
)][order(Battles, WR)]

x_labels <- auto_range_format(buckets.battles.career)
fill_labels <- percent_range_format(buckets.WR)

plot_marimekko(res, title, update,
    x_name = "Battles", fill_var = "WR", palette.fill = palette.WN8,
    x_labels = x_labels, fill_labels = fill_labels
)
```


## Average Tier

The following graph shows a histogram of share of players (y-axis) average tier (x-axis). Only players with more than `r min_battles.career` battles during their Blitz "career" are included.

```{r fig_career_player_avg_tier_histogram}
res <- stats.career[battles.career.all > min_battles.career,
    .("Average Tier" = sum(tier * battles.career) / first(battles.career.all)),
    by = account_id
]
plot_histogram(res, "Average Tier", update,
    "Average Tier", "Share of Players %",
    x_lims = c(1, 10), x_step = 1, y_step = 0.01
)
```

## WR vs. Average Tier

This graph shows player Career WR vs. average tier until the end of update `r update`. Minimum `r min_battles.career` battles required. 

```{r fig_career_WR_vs_avg_tier,warning=FALSE,message=FALSE}
res <- stats.career[battles.career.all > min_battles.career,
    .(
        "Career WR" = first(WR.career.all),
        "Average Tier" = sum(tier * battles.career) / first(battles.career.all)
    ),
    by = account_id
][order(`Career WR`)][sample(.N, min(.N, 50e3))]
plot_average_XY(res, "Player Career WR vs. Average Tier", update, "Average Tier", "Career WR",
    x_breaks = seq(1, 10), y_breaks = seq(0, 1, .1), y_pct = TRUE, y_lims = c(.3, .7), panel_top = TRUE
)
```

## Battles per Tier

This graph shows average number of career battles per tier.   

```{r fig_career_battles_per_tier}
res <- stats.career[, .(Battles = sum(battles.career)),
    by = .(account_id, tier)
][, .(Battles = mean(Battles)),
    by = .(Tier = tier)
][order(Tier)]
res <- prep_plot_tier(res, "Battles")
plot_col_continuous_1Y(res, "Average Battles per Tier", update, "Tier", "Battles", y_pct = FALSE, y_step = 500)
```


## Most popular Tanks by Players

This graph shows the tanks with the most players. This counts all the battles played until the end of the update. More [Tank Statistics here](../).

```{r fig_career_tanks_most_popular}
res <- head(stats.career[, .(
    "Average WR" = DT_ratio(wins.career, battles.career),
    "Battles/Player" = mean(battles.career),
    "Players" = uniqueN(account_id),
    "Premium" = first(is_premium)
),
by = name
][order(-Players)], n = 20)
res <- prep_plot_tank(res, "Players")

plot_col_discrete_1Y(res, "Most Popular Tanks", update, "Tank", "Players", fill_var = "Tank type", y_pct = FALSE)
```

### Most popular Tanks - Table

{{% expand "Show table" %}}
```{r career_tanks_most_popular, echo = FALSE}
md_table(res, update_path_lvl = 1, enough_players = tanks.enough_players)
```
{{% /expand %}}

## Most played Tanks

This graph shows the most played tanks by their owners during their career. More [Tank Statistics here](../).

```{r fig_career_tanks_most_battles}
res <- head(stats.career[, .(
    "Average WR" = DT_ratio(wins.career, battles.career),
    "Battles/Player" = mean(battles.career),
    "Battles" = sum(battles.career),
    "Players" = uniqueN(account_id),
    "Premium" = first(is_premium)
),
by = name
][order(-`Battles`)], n = 20)
res <- prep_plot_tank(res, "Battles")

plot_col_discrete_1Y(res, "Most Battles", update,
    "Tank", "Battles",
    fill_var = "Tank type",
    y_pct = FALSE, y_steps = 20
)
```
### Most played Tanks - Table

{{% expand "Show table" %}}
```{r career_tanks_most_battles, echo = FALSE}
md_table(res, update_path_lvl = 1, enough_players = tanks.enough_players)
```
{{% /expand %}}

## Most Battles by Player

This graph shows the most played tanks by their owners during their career (=battles/players). More [Tank Statistics here](../).

```{r fig_career_tanks_most_played}
res <- head(stats.career[, .(
    "Average WR" = DT_ratio(wins.career, battles.career),
    "Battles/Player" = mean(battles.career),
    "Players" = uniqueN(account_id),
    "Premium" = first(is_premium)
),
by = name
][order(-`Battles/Player`)], n = 20)
res <- prep_plot_tank(res, "Battles/Player")

plot_col_discrete_1Y(res, "Most Battles by Player", update, "Tank", "Battles/Player", fill_var = "Tank type", y_pct = FALSE, y_step = 100)
```

### Most Played Tanks - Table

{{% expand "Show table" %}}
```{r career_tanks_most_played, echo = FALSE}
md_table(res, update_path_lvl = 1, enough_players = tanks.enough_players)
```
{{% /expand %}}


```{r clean_up}
rm(list = var2rm)
```