---
title: "Update 6.10 stats added"
linktitle: "2020-06-17 Update 6.10 stats added"
date: `r today("UTC")`
publishdate: 2020-06-17
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "6.10" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver <- '6.10'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Stats for `r md_link_update(update_ver)` has been added to the site. How did the ATGM tanks 
actually perform? Did Sheridan deserve its upcoming nerf in `r md_link_update("7.0")`? 
(no, it was nowhere near the top...)


```{r fig_tanks_tier10_RelativeWR}
tank_type  	<- NULL
tierN 			<- 10
stats 			<- subset(stats.update.perf, tier == tierN)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

Was `r md_link_tank(tank_name="T92E1", update="6.10")` still one of the best 
performing `r md_link_update(update="6.10", link_text="tier IX tanks", rel_link="tanks/9/")`? 
(well, 15th and perfectly balanced)


```{r fig_tanks_tier9_RelativeWR}
tank_type  	<- NULL
tierN 			<- 9
stats 			<- subset(stats.update.perf, tier == tierN)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```


I also discovered a bug in the code (function params in wrong order) that has likely impact the earlier 
results to some extend by filtering out too many results. Fixed now after several hours of debugging...
