---
title: "Update 8.2 final stats added "
linktitle: "2021-09-18 Update 8.2 final stats added"
date: `r today("UTC")`
publishdate: 2021-09-18
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "8.2" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '8.2'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were `r auto_format(res$Battles)` battles by `r auto_format(res$Players)` 
players recorded in the database during the `r md_link_update(update=update_ver)`.

* The `r md_link(update=update_ver, link_text="TOP20 best performing tanks", rel_link="#highest-relative-wr")` 
list has not significant changes. `r md_link_tank(tank_names='Annihilator', update=update_ver)` 
was nerfed via MM in `r md_link_update(update="8.1")` and it has since dropped from the list. 
It is still insanely powerful tank, but meets always another Anni in the red team so easy farming 
days in completely broken tank are over. [Crocodile's tears](https://en.wikipedia.org/wiki/Crocodile_tears) from me, boys. 

* `r md_link_tank(tank_names='Dreadnought', update=update_ver)` - the new event tank 
based on `r md_link_tank(tank_names='Churchill Gun Carrier', update=update_ver)` 
- seems to perform great and it took the Top 5 spot right away. 

* Otherwise the list is full of the typical premium tanks like 
`r md_link_tank(tank_names='T28 Concept', update=update_ver)`, 
`r md_link_tank(tank_names='Object 252U', update=update_ver)` and 
`r md_link_tank(tank_names='AT 15A', update=update_ver)` that took the 3rd spot. 
The `r md_link_tank(tank_names='AT 15A', update=update_ver)` is played by quite small 
player population so that might create bias to the results. It might also be that the armor 
highlighting change in `r md_link_update(update="8.1")` has played to benefit well-armored 
tanks since pens now have a change to pen even the armor is shown red. 

* `r md_link_tank(tank_names='Emil I', update=update_ver)` is the best-performing 
Tech-tree tank at 4th place, but also the only Tech tree tank in Top 10. Talk about pay-to-win. 


```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver)
```

* `r md_link_tank(tank_names='Chimera', update=update_ver)` has dropped 
surprisingly low despite it has not received any nerfs. I am not certain why 
this has happened. This could be due to sensitivity of the Relative WR method 
itself or due changes of the tanks played at tier VIII introducing counter-forces 
to it. Good ideas are welcome! 

## Annihilator is still a great tank

*... Even it does not win much.*

* Just to highlight how has the "MM-nerf" impacted on the 
`r md_link_tank(tank_names='Annihilator', update=update_ver)`.
 It is now the 3rd *worst* performing 
 `r md_link_tier_tank_type(update=update_ver, tier=6, tank_type="Heavy Tank", append_text="heavy tank", rel_link="#highest-relative-wr")`
 in terms of relative WR. 

```{r fig_tanks_tier7_heavy_RelativeWR}
tank_type  	<- 'Heavy Tank'
tierN 				<- 7
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, tank_type = tank_type, tier = tierN)
```

* But the `r md_link_tank(tank_names='Annihilator', update=update_ver)` 
is still dealing disproportionate amount of damage and havoc at the battlefield.


```{r fig_tanks_tier7_HT_Anni_AvgDmg}
bin_breaks  <- seq(.25,.85, 0.05)
tank_type  	<- 'Heavy Tank'
tierN 			<- 7
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tier_tank_type_avg_dmg(stats = stats, tier = tierN, 
														tank_type = tank_type, 
 														update = update_ver)
```

* Well, Halloween is coming. Sealclubbers, get your wallets ready :-) 






