---
title: "Update 7.3 stats added "
linktitle: "2020-11-13 Update 7.3 stats added"
date: `r today("UTC")`
publishdate: 2020-11-13
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.3"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.3'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Stats for `r md_link_update(update_ver)` have been added. 

* Total 230M battles by 484k players recorded in the database during the 
`r md_link_update(update_ver)`. Please note, these are note all the WoT Blitz 
players, just those tracked by BlitzAnalysiz[]. 

* `r md_link_tank(tank_names='T28 Concept', update=update_ver)` and 
`r md_link_tank(tank_names='Chimera', update=update_ver)` continue to be 
the best performing tanks in the game. When looking into the details, it 
is clear that `r md_link_tank(tank_names='T28 Concept', update=update_ver)`'s 
performance in the hands of average & below-average players (strong armor) 
pushes its average Relative WR high. The tank is performing well, but relatively 
bit less well in the hands of very good players. This is likely due to its poor
mobility. At the moment the Relative WR data is not 
[stratified](https://en.wikipedia.org/wiki/Stratified_sampling). 
Stratified sampling would eliminate the impact of the differences in the 
tanks' player populations better and give more comparable view of the tanks' 
performance.

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

# Swedish heavy tank line

`r md_link_update(update=update_ver)` brought the Swedish heavy tanks. 
As it is often the case with new tank lines, those are first played 
with more experienced & better players distorting the average WR 
statistics for the tanks. `r md_link_tank(tank_names='Emil I', update=update_ver)` 
player population offers a great example:

```{r fig_player_base_Emil_I}
tank_id     <- get_tank_id('Emil I')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_player_base(stats = stats, tank_id = tank_id, 
                      title.avg = paste('Tier', get_tier_roman(tierN), tank_types), 
                      update = update_ver)
```

## Tier VI Strv 74

Of the Swedish line, the 
`r md_link_tier(update=update_ver, tier=6)` 
**`r md_link_tank(tank_names='Strv 74', update=update_ver)`** 
seems performing below the average. I liked it personally, but based on 
the numbers it does not perform that well. 

```{r fig_tank_relativeWR_Strv_74}
tank_id     <- get_tank_id('Strv 74')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```

## Tier VII Leo

The `r md_link_tier(update=update_ver, tier=7)` 
**`r md_link_tank(tank_names='Leo', update=update_ver)`** seems performing 
also below the average for the better players. I liked it personally, but 
maybe its lowish DPM (still higher than the T20) pushed the Relative WR down. 

```{r fig_tank_relativeWR_Leo}
tank_id     <- get_tank_id('Leo')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```

## Tier VIII Emil I

The `r md_link_tier(update=update_ver, tier=8)` 
**`r md_link_tank(tank_names='Emil I', update=update_ver)`** is the gem of 
the line and currently the best performing tier VIII _Tech Tree_ heavy tank. Players 
have been crying it needs to nerfed, but let's remember that the Emil I is only the 
`r md_link_tier_tank_type(update=update_ver, tier=8, tank_type = 'Heavy Tank', link_text="4th best performing tier VIII heavy tank", rel_link="#the-best-performing-tanks")`.
Its superior performance on the battlefield is also greatly contributed 
by its better-than-average player population (3.9% higher  average WR vs. all tier VIII heavy tanks).

```{r fig_tank_relativeWR_Emil_I}
tank_id     <- get_tank_id('Emil I')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```


```{r fig_tank_player_base_Emil_I}
tank_id     <- get_tank_id('Emil I')

plot_tank_player_base(stats = stats, tank_id = tank_id, update = update_ver)
```



## Tier IX Emil II 

The `r md_link_tier(update=update_ver, tier=9)` 
**`r md_link_tank(tank_names='Emil II', update=update_ver)`** performed very 
much the average. I would say the EMil II is _perfectly balanced_. 

```{r fig_tank_relativeWR_Emil_II}
tank_id     <- get_tank_id('Emil II')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```
## Tier X Kranvagn

The `r md_link_tier(update=update_ver, tier=10)` 
**`r md_link_tank(tank_names='Kranvagn', update=update_ver)`** was an disappointment 
for many and it performs the average (below the average for good players). WG 
often tends to launch new lines with borderline OP-performance. It might be 
that WG  thought the [Kranvagn](/update/`r update_ver`/10/tanks/4481/) has so 
much positives that players would play it in any case, and they decided to 
launch it as _balanced_. Launching a new line balanced feels almost like 
launching it _nerfed_ since the standard is borderline-OP. 

```{r fig_tank_relativeWR_Kranvagn}
tank_id     <- get_tank_id('Kranvagn')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- subset(stats.update.perf, tier == tierN & type == tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```
