```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = "svglite", fig.ext = "svgz")
# Checks
stopifnot(exists("target_page"))
update <- get_path_elem(target_page, 2)
preliminary <- is_preliminary(update)
tier <- get_path_elem_int(target_page, 3)
tierN <- tier
tier.roman <- get_tier_roman(tier)
min_battles.tier <- get_min_battles_tier(tier)
min_battles.tank <- floor(min_battles.tier / 2)
min_battles.grind <- get_grind_len(tier)
page_weight <- 10
stats.tier <- get_stats.update.tier(tierN)
var2rm <- c("res", "stats.tier")
```

---
title: "Tier `r tier.roman` player stats"
menutitle: "Players"
linktitle: "Tier `r tier.roman` player stats (`r update_version(update)`)"
date: `r today("UTC")`
author: Jylpah@gmail.com
disableToc: false
hidden: true
autohide: true
alwaysopen: false
output: md_document
weight: `r page_weight`
tags: [ "`r update`", "Tier `r tier.roman`", "Tier stats"  ]
---

`r update_if_final(update, '', '_Preliminary stats_')`

This page list statistics of players' battles at **tier `r tier.roman` during update `r update`**. 

## Current WR vs. Career Battles played

This graph shows players WR at the tier `r tier.roman` during the update `r update` vs. players' career battles. 

```{r fig_career_battles_vs_current_WR, message=FALSE}
x_name <- "Battles"
y_name <- "WR"
fill_name <- "WR"
title <- "Current WR by Career Battles"

res <- stats.tier[, .(
  "WR" = first(WR.global),
  "Battles" = first(battles.career)
),
by = account_id
][, .N, by = .(
  Battles = cut(Battles, breaks = buckets.battles.career, include.lowest = TRUE),
  WR = cut(WR, breaks = buckets.WR, include.lowest = TRUE)
)][order(Battles, WR)]

x_labels <- auto_range_format(buckets.battles.career)
fill_labels <- percent_range_format(buckets.WR)

plot_marimekko(res, title, update,
  x_name = "Battles", fill_var = "WR", palette.fill = palette.WN8,
  x_labels = x_labels, fill_labels = fill_labels, tier = tier
)
```

## Battles per Player

Number of battles fought per player during the update `r update`. 

```{r fig_tier_battle_count_histogram}
res <- stats.tier[, .(Battles = sum(all.battles)), by = account_id]

if (tier > 5) {
  x_breaks <- seq(0, 1000, 100)
  bin_breaks <- seq(0, 1000, 25)
} else {
  x_breaks <- seq(0, 500, 50)
  bin_breaks <- seq(0, 500, 25)
}


plot_histogram(res, "Battles played per Players", update,
  x_name = "Battles", y_name = "Share of Players %",
  bin_breaks = bin_breaks, x_signif = 2,
  y_pct = TRUE, y_signif = 2, x_breaks = x_breaks, mean = TRUE, tier = tier
)

s <- stats.tier[, .(Battles = sum(all.battles)), by = account_id][, .(mean = mean(Battles), median = median(Battles), max = max(Battles))]
```

On average, players played `r as.integer(s$mean)` battles. Median was `r s$median` and the largest number of battles recorded by a single player (in the dataset) during the update `r update` was `r auto_format(s$max, digits = 10, no_sfx=TRUE)` battles. The following tables shows battle counts by N% most inactive players during the update. 

### Battles per Player table

The table below shows the (max) number of battles played during `r update` by the X% most _inactive_ players. A reading tip: 10% most _active_ players played more than the 90% most _inactive_ players.

{{% expand "Show table" %}}
```{r tier_battle_count_summary, echo = FALSE}
md_table_histogram(
  stats.tier[, .(Battles = sum(all.battles)),
    by = account_id
  ][, Battles],
  "Battles",
  breaks = buckets.battles, lims = c(0, 1000)
)
```
{{% /expand %}}


## Player WR distribution

### Players with `r min_battles.tier`+ battles in maxed-out tanks 

The following graph shows a histogram of players (y-axis) with certain WR during the update `r update` (x-axis). This graph includes all the players who have played more than `r min_battles.tier` battles during the update. 

```{r fig_tier_player_WR_histogram}
res <- stats.tier[DT_filter_enough_battles.tier(stats.tier),
  .(WR = first(WR.tier.maxed), Battles = first(battles.tier.maxed)),
  by = account_id
][Battles > min_battles.tier]
title <- get_plot_title_subtitle("Player WR distribution", "Active players, maxed-out tanks")
plot_histogram(res, title,
  update,
  x_name = "WR", y_name = "Share of Players",
  x_lims = c(0, 1), x_step = 0.1, x_pct = TRUE,
  y_pct = TRUE, y_steps = 10, y_signif = 2, bins = 100, tier = tier
)
```

{{% expand "Show table" %}}
```{r tier_player_WR_histogram, echo = FALSE}
md_table_histogram(
  stats.tier[DT_filter_enough_battles.tier(stats.tier),
    .(WR = first(WR.tier.maxed)),
    by = account_id
  ][, WR],
  "WR",
  breaks = seq(0, 1, 0.01), lims = c(.2, .85)
)
```
{{% /expand %}}

### Player WR distribution (all players)

The following graph shows a histogram of players (y-axis) with certain WR during the update `r update` (x-axis). This graph includes all the players who have played during the update, even a single game. Therefore there are peaks around 25%, 33%, 50%, 67% and 75% and players with 0% or 100% WR. 

```{r fig_tier_player_WR_histogram_unfiltered}
res <- stats.tier[,
  .(WR = first(WR.tier.all), Battles = first(battles.tier.all)),
  by = account_id
]

title <- get_plot_title_subtitle("Player WR distribution", "All players")


plot_histogram(res, title, update,
  x_name = "WR", y_name = "Share of Players",
  x_lims = c(0, 1), x_step = 0.1, x_pct = TRUE,
  y_pct = TRUE, y_steps = 10, y_signif = 2, bins = 100, tier = tier
)
```

## Average damage distribution

The following graph shows a histogram of players' average damage. Y-axis shows the share of players (%) with certain certain average damage during the update `r update` (x-axis). This graph includes all the players who have played more than `r min_battles.tier` battles with a maxed-out tank during the update. 

```{r fig_tier_player_avg_dmg_histogram}
res <- stats.tier[DT_filter_enough_battles.tier(stats.tier),
  .("Average Damage" = first(avg_dmg.tier.maxed), Battles = first(battles.tier.maxed)),
  by = account_id
][Battles > min_battles.tier]

title <- get_plot_title_subtitle("Player Average Damage distribution", "Active players, Maxed-out tanks")

plot_histogram(res, title, update,
  x_name = "Average Damage", y_name = "Share of Players",
  x_quantiles = list(NULL, .999),
  x_pct = FALSE,
  y_pct = TRUE, y_steps = 10, y_signif = 2,
  bins = 100, tier = tier
)
```

{{% expand "Show table" %}}
```{r tier_player_avg_dmg_histogram, echo = FALSE}
x_breaks <- get_breaks(0, quantile(res$`Average Damage`, .9999, na.rm = TRUE), steps = 20)
x_breaks <- x_breaks$breaks

md_table_histogram(res$`Average Damage`, "Average Damage",
  breaks = x_breaks
)
```
{{% /expand %}}


## Average Damage + kills per battle vs. WR

```{r fig_tier_WR_vs_avg_dmg_kpb}
x_name <- "Average Damage"
y_name <- "Kills/Battle"
z_name <- "WR"
res <- stats.tier[DT_filter_enough_battles.tier(stats.tier),
  .(
    "Average Damage" = first(avg_dmg.tier.maxed),
    "Kills/Battle" = sum(all.frags) / sum(all.battles),
    "WR" = first(WR.tier.maxed),
    "Battles" = first(battles.tier.maxed)
  ),
  by = account_id
]

title <- get_plot_title_subtitle(
  "WR vs. Average Damage + Kills per Battle",
  "Active players, Maxed-out tanks, Tier average"
)

plot_contour_discrete(res, title, update,
  x_name, y_name, z_name,
  weights = "Battles",
  col.palette = palette.WN8,
  col.levels = buckets.WR,
  tier = tierN
)
```


## Share of Battles per Nation per Vehicle Class

This chart shows share of battles per nation per vehicle class at tier `r tier.roman`. 

```{r fig_tier_battles_nation_vehicle_class}
y_name <- "Battles"
x_name <- "Nation"
fill_name <- "Vehicle Class"
title <- get_plot_title_share_of_by_by(y_name, x_name, fill_name)
res <- stats.tier[, .(N = sum(all.battles)),
  by = .(Nation = nation, "Vehicle Class" = type)
][order(Nation, `Vehicle Class`)]
plot_marimekko(res, title, update, x_name, fill_name, palette.fill = palette.vehicle_class)
```

## Player WR per Nation

```{r fig_tier_WR_per_nation}
res <- stats.tier[DT_filter_enough_battles.tier(stats.tier),
  .(WR = mean(WR.tier.maxed)),
  by = .(nation, account_id)
][, .N, by = .(Nation = nation, WR = cut(WR, breaks = buckets.WR, include.lowest = TRUE))][order(Nation, WR)]
plot_col_share_discrete(res, "Player WR per Nation", update,
  x_name = "Nation", fill_var = "WR", tier = tier, y_buckets = buckets.WR
)
```

```{r clean_up}
rm(list = var2rm)
```