```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150,echo = FALSE, warning=FALSE, dev = 'svglite', fig.ext = 'svgz');
stopifnot(exists('target_page'))
update 			<- get_path_elem(target_page, 2)
preliminary <- is_preliminary(update)
tank_id 		<- get_path_elem_int(target_page,5)
tier 				<- get_path_elem_int(target_page,3)
tierN 			<- tier
tier.roman 	<- get_tier_roman(tier)
tank_ID 		<- tank_id
tank_name 	<- get_tank_name(tank_id)
tank_type 	<- get_tank_type(tank_id)
tank_nation <- get_tank_nation(tank_id)
tank_is_premium 			<- get_tank_is_premium(tank_id)
tank_nation.str 			<- Nations.str[[as.integer(tank_nation)]]
min_battles.tier 			<- get_min_battles_tier(tier)
min_battles.tank 			<- floor(min_battles.tier / 2)
min_battles.grind 		<- get_grind_len(tier)
stats.tier 		<- get_stats.update.tier(tierN)
stats.tier 		<- get_stats_tank_perf(stats.tier)
stats.tier.type <- subset(stats.tier, type == tank_type)
stats.update.tank 		<- get_stats_tank(tank_ID)
var2rm 								<- c('res', 'stats.tier','stats.tier.type', 'stats.update.tank')
if (! has_enough_players(stats.update.tank, tank_ID)) {
        knit_exit(DELETE_PAGE)
}
if (nrow(stats.update.tank) > 2000) {
        bin_breaks = seq(.25,.85, 0.05)
} else {
        bin_breaks = seq(.25, .85, 0.1)
}
```

---
title: "`r get_tank_name(tank_id)`"
date: `r today("UTC")`
author: Jylpah@gmail.com
disableToc: false
output: md_document
tags: [ "`r update`", "Tier `r tier.roman`", "Tanks/Tier", "`r tank_type`", "`r get_tank_name(tank_id)`" ]
alwaysopen: false
hidden: true
autohide: false
---

`r update_if_final(update, '', '_Preliminary stats_')`

`r tank_name` is a `r tank_nation.str` [Tier `r tier.roman`](../../) 
`r if (tank_is_premium) {'[premium](../../premium-tanks/) '}``r md_link_tank_type(tank_id, '../../')`. 

## Player Population

This graphs compare's the tank's player population by _WR at Tier_ to other same tier `r tank_type`s.

```{r fig_tank_player_base, warning=FALSE}
res <- stats.tier.type[ DT_filter_enough_battles.rWR(stats.tier.type), 
                          .('WR at Tier' = WR.tier.maxed, 
                            'Tank' = name)]

title <- 'Player Base Skill-level (WR at the Tier)'

perf_measure <- 'Players'
by_measure <- 'WR at Tier'

title.tier.tank_type <- paste0('Tier ', tier.roman, ' ',tank_type, 's')

plot_histogram_continuous(res, title, update, 
                          by_measure, perf_measure, 
													fill_var ='Tank', fill_elems = tank_name, 
													x_step = 0.05,y_step = 0.02,
													x_pct = TRUE, y_pct = TRUE, x_signif = 3, 
													palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
													palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
													avg_name = title.tier.tank_type, mean = FALSE, tier = tierN)
```

## Relative WR vs. Player Skill-level

This graphs shows how well players of different skill-level (measured by _WR at Tier_) 
perform in the tank vs. their other same tier, same type tanks. 

```{r fig_tank_relativeWR, warning=FALSE}
 
perf_measure <- 'Relative WR'
by_measure <- 'WR at Tier'

res <- stats.tier.type[ DT_filter_enough_battles.rWR(stats.tier.type), 
                          .('WR at Tier' = WR.tier.maxed, 
                            'Relative WR' = rWR), 
                          by=.(Player = account_id, Tank = name)]

title.tier.tank_type <- paste0('Tier ', tier.roman, ' ',tank_type, 's')

title <- get_plot_title_perf_by(tank_name, perf_measure, 'WR at Tier')

plot_average_Y(res, title, update, by_measure, perf_measure,
               fill_var = 'Tank', fill_elems = tank_name,
               bin_breaks = bin_breaks,
               x_pct = TRUE, y_step = 0.01, y_pct = TRUE,
               palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
               palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
               avg_name = title.tier.tank_type, mean = TRUE, tier = tier)

```


# Stat levels vs. WR

These graphs players _input-stats_ vs. the WR they have reached with the tank. 
The players' averages over all the same tier tanks is shown in grey. 
The bars show the 20-80% stat levels within the WR bucket 
(20% of players will have higher/lower stats than these).  

## Average Damage

```{r fig_tank_avg_dmg, warning=FALSE}
 
perf_measure <- 'Average Damage'
by_measure <- 'WR at Tier'

res <- stats.tier[ DT_filter_enough_battles.rWR(stats.tier), 
                          .('WR at Tier' = WR.tier.maxed,
                            #'WR (Tank)' = WR, 
                            'Average Damage' = avg_dmg), 
                          by=.(Player = account_id, Tank = name)]

title.tier.avg <- paste0('Tier ', tier.roman, ' Average')

title <- get_plot_title_perf_by(tank_name, perf_measure, 'WR')

plot_quantile_Y(res, title, update, by_measure, perf_measure, 
               fill_var ='Tank', fill_elems = tank_name, 
               bin_breaks = bin_breaks, x_pct = TRUE, y_pct = FALSE,
               palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
               palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
               avg_name = title.tier.avg, tier = tier)

```

## Kills per Battle

```{r fig_tank_avg_kills, warning=FALSE}

perf_measure <- 'Kills per Battle'
by_measure <- 'WR at Tier'

res <- stats.tier[ DT_filter_enough_battles(stats.tier), 
                          .( 'WR at Tier' = WR.tier.maxed,
                             #'WR (Tank)' = WR,
                             'Kills per Battle' = avg_kills), 
                          by=.(Player = account_id, Tank = name)]

title.tier.avg <- paste0('Tier ', tier.roman, ' Average')

title <- get_plot_title_perf_by(tank_name, perf_measure, 'WR')

plot_quantile_Y(res, title, update, by_measure, perf_measure, 
                fill_var ='Tank', fill_elems = tank_name, 
                bin_breaks = bin_breaks, x_pct = TRUE, y_pct = FALSE,
                palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
                palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
                avg_name = title.tier.avg, tier = tier)

```

## Spot Rate

```{r fig_tank_spot_rate, warning=FALSE}

perf_measure <- 'Spot Rate'
by_measure <- 'WR at Tier'

res <- stats.tier[  DT_filter_enough_battles(stats.tier), 
                           .( 'WR at Tier' = WR.tier.maxed,
                              #'WR (Tank)' = WR,
                              'Spot Rate' = spot_rate), 
                           by=.(Player = account_id, Tank = name)]

title.tier.avg <- paste0('Tier ', tier.roman, ' Average')

title <- get_plot_title_perf_by(tank_name, perf_measure, 'WR')

plot_quantile_Y(res, title, update, by_measure, perf_measure, 
                fill_var ='Tank', fill_elems = tank_name, 
                bin_breaks = bin_breaks, x_pct = TRUE, y_pct = FALSE,
                palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
                palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
                avg_name = title.tier.avg, tier = tier)
```


## Hit Rate

```{r fig_tank_hit_rate, warning=FALSE}

perf_measure <- 'Hit Rate'
by_measure <- 'WR at Tier'

res <- stats.tier[  DT_filter_enough_battles(stats.tier), 
                           .( 'WR at Tier' = WR.tier.maxed,
                              # 'WR (Tank)' = WR,
                              'Hit Rate' = hit_rate), 
                           by=.(Player = account_id, Tank = name)]

title.tier.avg <- paste0('Tier ', tier.roman, ' Average')

title <- get_plot_title_perf_by(tank_name, perf_measure, 'WR')

plot_quantile_Y(res, title, update, by_measure, perf_measure, 
                fill_var ='Tank', fill_elems = tank_name, 
                bin_breaks = bin_breaks, x_pct = TRUE, y_step = 0.025, y_pct = TRUE,
                palette.fill = palette.vehicle_class[[get_tank_type(tank_id)]],
                palette.annotate = palette.vehicle_class.lines[[get_tank_type(tank_id)]],
                avg_name = title.tier.avg, tier = tier)
```


# WR analysis

These graphs shows how different stat-pairs (X/Y) relate to WR (the color coding).  

## Average Damage + kills per Battle vs. WR

This graphs shows Average WR as a function of Average Damage and Kill per Battle. 

```{r fig_tank_WR_vs_avg_dmg_kills, warning=FALSE}
x_name = 'Average Damage'
y_name = 'Kills/Battle'
z_name = 'WR'
res <- stats.update.tank[ ,
              .('Average Damage' = avg_dmg, 
                'Kills/Battle' = avg_kills, 
                'WR' = WR, 
                'Battles' = all.battles)]

title <- get_plot_title_tank_z_is_xy(tank_name, z_name, x_name, y_name)

plot_contour_discrete(res, title, update, 
                      x_name, y_name, z_name, weights = 'Battles', 
                      col.palette = palette.WN8, 
                      col.levels = buckets.WR, 
                      tier = tierN)

```

## Spot Rate + Survival Rate vs. WR

```{r fig_tank_WR_vs_spots_survival, warning=FALSE}
x_name = 'Survival Rate'
y_name = 'Spot Rate'
z_name = 'WR'
res <- stats.update.tank[,
              .( 'Survival Rate' = survival_rate, 
                'Spot Rate' = spot_rate, 
                'WR' = WR, 
                'Battles' = all.battles)]

title <- get_plot_title_tank_z_is_xy(tank_name, z_name, x_name, y_name)

plot_contour_discrete(res, title, update, 
                      x_name, y_name, z_name, weights = 'Battles', 
                      col.palette = palette.WN8, 
                      col.levels = buckets.WR, 
                      x_pct = TRUE , tier = tier)

```


## Spot Rate + Average Battle Lifetime vs. WR


```{r fig_tank_WR_vs_spots_lifetime, warning=FALSE}
x_name = 'Average Battle Lifetime'
y_name = 'Spot Rate'
z_name = 'WR'
res <- stats.update.tank[, 
              .( 'Average Battle Lifetime' = battle_life_time / all.battles,
                'Spot Rate' = spot_rate, 
                'WR' = WR, 
                'Battles' = all.battles)][`Average Battle Lifetime` <= 7*60]

title <- get_plot_title_tank_z_is_xy(tank_name, z_name, x_name, y_name)

plot_contour_discrete(res, title, update, 
                      x_name, y_name, z_name, weights = 'Battles', 
                      col.palette = palette.WN8, 
                      col.levels = buckets.WR, 
                      x_pct = FALSE, tier = tier)

```


## Shots/Battle + Average Battle Lifetime vs. WR


```{r fig_tank_WR_vs_shots_lifetime, warning=FALSE}
x_name = 'Average Battle Lifetime'
y_name = 'Shots/Battle'
z_name = 'WR'
res <- stats.update.tank[, 
              .( 'Average Battle Lifetime' = battle_life_time / all.battles,
                'Shots/Battle' = all.shots/all.battles,
                'WR' = WR, 
                'Battles' = all.battles)][`Average Battle Lifetime` <= 7*60]

title <- get_plot_title_tank_z_is_xy(tank_name, z_name, x_name, y_name)

plot_contour_discrete(res, title, update, 
                      x_name, y_name, z_name, weights = 'Battles', 
                      col.palette = palette.WN8, 
                      col.levels = buckets.WR, 
                      x_pct = FALSE, 
                      tier = tier)
```


## Hit Rate + Shots/Battle vs. WR


```{r fig_tank_WR_vs_hit_rate_shots, warning=FALSE}
x_name = 'Shots/Battle'
y_name = 'Hit Rate'
z_name = 'WR'
res <- stats.update.tank[, 
              .('Hit Rate' = hit_rate, 
                'Shots/Battle' = all.shots/all.battles,
                'WR' = WR, 
                'Battles' = all.battles)]

title <- get_plot_title_tank_z_is_xy(tank_name, z_name, x_name, y_name)

plot_contour_discrete(res, title, update, 
                      x_name, y_name, z_name, weights = 'Battles', 
                      col.palette = palette.WN8, 
                      col.levels = buckets.WR, 
                      y_pct = TRUE, 
                      tier = tier)

```

```{r clean_up}
rm(list=var2rm)
```
