---
title: "Update 7.5 final stats added "
linktitle: "2021-01-31 Update 7.5 final stats added"
date: `r today("UTC")`
publishdate: 2021-01-31
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.5"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver <- '7.5'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)
```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were mind-blowing 452M battles by 610k players recorded in the 
database during the `r md_link_update(update=update_ver)`. These are by far the 
largest numbers ever record at BlitzAnalysiz[]. Please note, these are not 
all the WoT Blitz players, just those tracked by BlitzAnalysiz[]. 

* `r md_link_tank(tank_names='EMIL 1951', update=update_ver)` took straight 
away the second spot pushing `r md_link_tank(tank_names='Maus', update=update_ver)`, 
the best performing Tech tree tank, out of TOP 5. Great, people get bang 
for their rubles. Never mind the tank balance. 

* Otherwise the top spots went to tanks with great "balance" of armor, mobility and 
firepower such as `r md_link_tank(tank_names='T28 Concept', update=update_ver)`, 
`r md_link_tank(tank_names='T54E2', update=update_ver)` and 
`r md_link_tank(tank_names='Annihilator', update=update_ver)`.

```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* **New Relative WR by player skill-level charts** added for the 
`r md_link_update(update=update_ver, link_text="main tank stats", rel_link="#relative-wr-by-player-skill-level")`
and `r md_link_update_tier(update=update_ver, tier=10, link_text="tier tank stats", rel_link="#relative-wr-by-player-skill-level")`. 
There are three player skill-level buckets measured as _WR at the tier_: 0-45%, 45-55% and 55%+. 

```{r fig_tanks_top_RelativeWR_tier10}
stats <- get_stats.update.tier(tierN = 10, DT = stats.update.perf)
stats <- subset(stats, WR.tier.maxed >= .55 & WR.tier.maxed < .65)
plot_tier_tank_type_relativeWR(stats = stats, update = update_ver, 
																tier=10, topN = topN, 
																subtitle = paste("Players with 55-65% WR at tier X\n", 'update', update_ver));
```
