```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE, dev = "svglite", fig.ext = "svgz")
# Checks
stopifnot(exists("target_page"))
page_level_update <- 2
update <- get_path_elem(target_page, 2)
preliminary <- is_preliminary(update)
tier <- get_path_elem_int(target_page, 3)
tierN <- tier
tier.roman <- get_tier_roman(tier)
tank_type <- "Premium Tank"
topN <- topN.default
min_battles.tier <- get_min_battles_tier(tier)
min_battles.tank <- floor(min_battles.tier / 2)
min_battles.grind <- get_grind_len(tier)

if (!exists("stats.tier")) {
  cols.sel <- c(
    "account_id", "tank_id", "battles", "battles.career",
    "region", "name", "tier", "nation", "type", "is_premium", "WR",
    "rWR", "WR.tier.maxed", "battles.tier.maxed", "avg_dmg", "avg_kills",
    "spot_rate", "hit_rate"
  )
  stats.tier.premiums <- ds_load_ts_update(update,
    tank_tier = tierN,
    premium = TRUE,
    cols = cols.sel
  )
} else {
  stats.tier.premiums <- subset(stats.tier, is_premium == TRUE)
}
stats.tier.premiums.perf <- get_stats_tank_perf(ds_load_ts_maxed(update,
  tank_tier = tierN,
  premium = TRUE,
  cols = cols.sel
))
var2rm <- c("res", "stats.tier.premiums", "stats.tier.premiums.perf")
tanks.enough_players <- get_tanks_enough_players(stats.tier.premiums.perf)
```

---
title: "Tier `r get_tier_roman(tier)` Premium Tanks"
menutitle: "Premium Tanks"
date: `r today("UTC")`
author: Jylpah@gmail.com
disableToc: false
output: md_document
weight: 5
description: "Stats of tier `r tier.roman` premium tanks in World of Tanks Blitz. Update `r update`"
tags: [ "`r update`", "Tier `r tier.roman`", "Tanks/Tier"]
alwaysopen: false
hidden: true
autohide: true
---

`r update_if_final(update, '', '_Preliminary stats_')`

```{r, results='asis'}
cat(md_hugo_expand("Show Tanks"))

tank_list <- get_tank_list(stats = stats.tier.premiums, tank_tier = tierN, premium = TRUE)
cat(md_tank_list(tank_list, update_path_lvl = page_level_update, enough_players = tanks.enough_players), sep = "\n")
cat(md_hugo_expand(close = TRUE))
```

All the graphs are based on battles played during update `r update` only (not cumulative data).

## The Best Performing Tanks

### Highest Relative WR

The graph shows tier [`r tier.roman`](..) `r tank_type`s by _Relative WR_. That is the average of players' WR in a 
tank compared to their average WR at the tier (in all same tier tanks). Relative WR is a measure of the performance/strength of the tank.

{{% expand "Show details" %}}
* All the statistics are about battles fought during the update `r update` only.
* The graph shows averages over all the player skill-levels. Well-armored tanks tend to do better in the hands of less-skilled players and thus those tanks tend to have higher (average) Relative WR even in the hands of skilled players those could do relatively worse.
* The impact of "Stock-grind battles" is reduced based on tier-specific requirement for total battles at the end of the update. Only players with more than `r floor(min(min_battles.grinds))`-`r floor(max(min_battles.grinds))` (depending on the tier) battles in a tank _in the end of the update_ are included to eliminate the impact of the first battles in the tank (with sub-100% crew / modules).
* The players need to have `r min(min_battles.tanks)`-`r max(min_battles.tanks)` battles in a tank and `r min(min_battles.tiers)`-`r max(min_battles.tiers)` battles at the tier during the update.
* **Average WR** is the players's average WR in the tank
* **Player WR at Tier** is the average WR of the players of the tank at the tier. Since different tiers have different difficulty, it is more meaningful to compare players' performance in the same tier tanks.
{{% /expand %}}

```{r fig_tanks_tier_premium_Relative_WR}
res <- stats.tier.premiums.perf[DT_filter_enough_battles.rWR(stats.tier.premiums.perf),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Vehicle Class" = first(type)
  ),
  by = name
][(Players >= min_players.tank)][order(-`Relative WR`)]

## No data >> EXIT
if (nrow(res) == 0) {
  knitr::knit_exit(DELETE_PAGE)
}

x_name <- "Tank"
y_name <- "Relative WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = TRUE, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = TRUE, top = TRUE, tier = tier
)
```

####  Relative WR - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_Relative_WR, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}

### Relative WR by player skill-level

Players' average WR at the tier is used as a measure for players' skill.

{{% expand "Relative WR - 65%+ players" %}}
```{r fig_tanks_tier_premium_Relative_WR_topN_65_}
res <- stats.tier.premiums.perf[
  DT_filter_enough_battles.rWR(stats.tier.premiums.perf) &
    (WR.tier.maxed > .65),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Vehicle Class" = first(type)
  ),
  by = name
][(Players >= min_players.tank)][order(-`Relative WR`)]

if (nrow(res) > 0) {
  x_name <- "Tank"
  y_name <- "Relative WR"
  res <- prep_plot_tank(res, y_name)
  title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
  title <- get_plot_title_subtitle(title, "Player WR at tier 65+%")
  plot_col_discrete_1Y(res, title, update, x_name, y_name,
    fill_var = "Vehicle Class",
    y_pct = TRUE, top = TRUE, tier = tier
  )
}
```
```{r tanks_tier_premium_Relative_WRN_65_, results='asis'}
if (nrow(res) == 0) {
  cat("Not enough players to calculate Relative WR\n")
}
```
{{% /expand %}}

{{% expand "Relative WR - 55-65% players" %}}
```{r fig_tanks_tier_premium_Relative_WR_topN_55_65}
res <- stats.tier.premiums.perf[
  DT_filter_enough_battles.rWR(stats.tier.premiums.perf) &
    (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Vehicle Class" = first(type)
  ),
  by = name
][(Players >= min_players.tank)][order(-`Relative WR`)]

if (nrow(res) > 0) {
  x_name <- "Tank"
  y_name <- "Relative WR"
  res <- prep_plot_tank(res, y_name)
  title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
  title <- get_plot_title_subtitle(title, "Player WR at tier 55-65%")
  plot_col_discrete_1Y(res, title, update, x_name, y_name,
    fill_var = "Vehicle Class",
    y_pct = TRUE, top = TRUE, tier = tier
  )
}
```
```{r tanks_tier_premium_Relative_WRN_55_65, results='asis'}
if (nrow(res) == 0) {
  cat("Not enough players to calculate Relative WR\n")
}
```
{{% /expand %}}


{{% expand "Relative WR - 45-55% players" %}}
```{r fig_tanks_tier_premium_Relative_WR_topN_45_55}
res <- stats.tier.premiums.perf[
  DT_filter_enough_battles.rWR(stats.tier.premiums.perf) &
    (WR.tier.maxed > .45) & (WR.tier.maxed <= .55),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Vehicle Class" = first(type)
  ),
  by = name
][(Players >= min_players.tank)][order(-`Relative WR`)]

if (nrow(res) > 0) {
  x_name <- "Tank"
  y_name <- "Relative WR"
  res <- prep_plot_tank(res, y_name)
  title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
  title <- get_plot_title_subtitle(title, "Player WR at tier 45-55%")
  plot_col_discrete_1Y(res, title, update, x_name, y_name,
    fill_var = "Vehicle Class",
    y_pct = TRUE, top = TRUE, tier = tier
  )
}
```
```{r tanks_tier_premium_Relative_WRN_45_55, results='asis'}
if (nrow(res) == 0) {
  cat("Not enough players to calculate Relative WR\n")
}
```
{{% /expand %}}

{{% expand "Relative WR - 0-45% players" %}}
```{r fig_tanks_tier_premium_Relative_WR_topN_0_45}
res <- stats.tier.premiums.perf[
  DT_filter_enough_battles.rWR(stats.tier.premiums.perf) &
    (WR.tier.maxed <= .45),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Vehicle Class" = first(type)
  ),
  by = name
][(Players >= min_players.tank)][order(-`Relative WR`)]

if (nrow(res) > 0) {
  x_name <- "Tank"
  y_name <- "Relative WR"
  res <- prep_plot_tank(res, y_name)
  title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
  title <- get_plot_title_subtitle(title, "Player WR at tier 0-45%")
  plot_col_discrete_1Y(res, title, update, x_name, y_name,
    fill_var = "Vehicle Class",
    y_pct = TRUE, top = TRUE, tier = tier
  )
}
```
```{r tanks_tier_premium_Relative_WRN_0_45, results='asis'}
if (nrow(res) == 0) {
  cat("Not enough players to calculate Relative WR\n")
}
```
{{% /expand %}}


## Average WR

This graph shows [`r tier.roman`](..) `r tank_type`s ranked by players' average WR in the tanks. **Player WR** denotes the tank's players' average WR across all the tier `r tier.roman` tanks during the update. Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.

```{r fig_tanks_tier_premium_WR}
res <- stats.tier.premiums.perf[, .(
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-`Average WR`)]
x_name <- "Tank"
y_name <- "Average WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = TRUE, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = TRUE, top = TRUE, tier = tier
)
```

#### Average WR - Table

**Average WR** denotes average WR in a tank across all the players during the update. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Show table" %}}
```{r tanks_tier_premium_WR, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Average Damage

This graph shows [`r tier.roman`](..) `r tank_type`s ranked by players' average damage in the tanks.

```{r fig_tanks_tier_premium_avg_dmg}
res <- stats.tier.premiums.perf[, .(
  "Average Damage" = mean(avg_dmg),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-`Average Damage`)]
x_name <- "Tank"
y_name <- "Average Damage"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = TRUE, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = FALSE, top = TRUE, tier = tier, y_steps = 20
)
```

#### Average Damage - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_avg_dmg, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Average Kills/Battle

This graph shows [`r tier.roman`](..) `r tank_type`s ranked by players' average kills per battle.

```{r fig_tanks_tier_premium_avg_kills}
res <- stats.tier.premiums.perf[, .(
  "Average Kills/Battle" = mean(avg_kills),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-`Average Kills/Battle`)]
x_name <- "Tank"
y_name <- "Average Kills/Battle"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = top, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = FALSE, top = top, tier = tier, y_step = 0.1
)
```

#### Average Kills/Battle - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_avg_kills, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Spot Rate

This graph shows [`r tier.roman`](..) `r tank_type`s ranked by players' spot rate in the tanks.

```{r fig_tanks_tier_premium_spot_rate}
res <- stats.tier.premiums.perf[, .(
  "Spot Rate" = mean(spot_rate, na.rm = TRUE),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-`Spot Rate`)]

x_name <- "Tank"
y_name <- "Spot Rate"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = top, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = FALSE, top = top, tier = tier, y_signif = 3
)
```

#### Spot Rate - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_spot_rate, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Hit Rate

This graph shows [`r tier.roman`](..) `r tank_type`s ranked by players' hit rate in the tanks.

```{r fig_tanks_tier_premium_hit_rate}
res <- stats.tier.premiums.perf[, .(
  "Hit Rate" = mean(hit_rate, na.rm = TRUE),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-`Hit Rate`)]

x_name <- "Tank"
y_name <- "Hit Rate"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = top, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name,
  fill_var = "Vehicle Class",
  y_pct = TRUE, top = top, tier = tier, y_step = 0.1, y_signif = 3
)
```

#### Hit Rate - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_hit_rate, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Most popular Tanks

This graph shows most popular tier [`r tier.roman`](..) `r tank_type`s tanks by players.

```{r fig_tanks_tier_premium_most_popular}
res <- stats.tier.premiums[, .(
  "Players" = uniqueN(account_id),
  "Battles" = sum(battles),
  "Battles/Player" = mean(battles),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-Players)]

x_name <- "Tank"
y_name <- "Players"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = top, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Vehicle Class", y_pct = FALSE, top = top, tier = tier, y_steps = 10)
```

## Most played Tanks

This graph shows the most played tier [`r tier.roman`](..) `r tank_type`s by number of battles during the update `r update`.

```{r fig_tanks_tier_premium_most_played}
res <- stats.tier.premiums[, .(
  "Players" = uniqueN(account_id),
  "Battles" = sum(battles),
  "Battles/Player" = mean(battles),
  "Average WR" = mean(WR),
  "Player WR at Tier" = mean(WR.tier.maxed, na.rm = TRUE),
  "Vehicle Class" = first(type)
),
by = name
][(Players >= min_players.tank)][order(-Battles)]
x_name <- "Tank"
y_name <- "Battles"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tank_type(y_name, tank_type, top = top, topN = NULL)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Vehicle Class", y_pct = FALSE, top = top, tier = tier, y_steps = 10)
```

### Most Played Tanks - Table

{{% expand "Show table" %}}
```{r tanks_tier_premium_most_played, echo = FALSE}
md_table(res, update_path_lvl = page_level_update, enough_players = tanks.enough_players)
```
{{% /expand %}}

```{r clean_up, include=FALSE}
rm(list = var2rm)
gc(verbose = FALSE)
```
