```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 8, fig.height = 6, dpi = 150, echo = FALSE,
  dev = "svglite", fig.ext = "svgz"
)
# Checks
stopifnot(exists("target_page"))
stopifnot(exists("updates"))
# stopifnot(exists("stats.update"))
update <- get_path_elem(target_page, 2)
cols.sel <- c(
  "account_id", "tank_id", "battles", "battles.career", "wins", "name", "tier",
  "is_premium", "type", "WR", "rWR", "tanks.tier.maxed", "WR.tier.maxed",
  "WR.update", "avg_dmg", "damage_dealt", "avg_kills", "spot_rate",
  "hit_rate"
)
if (exists("stats.update")) {
  rm(stats.update, stats.stats.update.perf)
}

# count all players
df.all <- ds_load_ts_update(update, cols = c("account_id", "battles"))
Players <- uniqueN(df.all$account_id)
Battles <- sum(df.all$battles)
rm(df.all)
gc(verbose = FALSE)

# load stats
stats.update.perf <- get_stats_tank_perf(ds_load_ts_maxed(update, cols = cols.sel))
stats.update <- ds_load_ts_update(update, cols = cols.sel)

var2rm <- c("res", "stats.update.perf", "stats.update")
tanks.enough_players <- get_tanks_enough_players(stats.update.perf)
page_weight <- -match(update, updates$Release)
preliminary <- is_preliminary(update)
```

---
title: "Update `r update_version(update)`"
menutitle: "Update `r update_version(update)`"
date: `r today("UTC")`
author: Jylpah@gmail.com
disableToc: false
output: md_document
weight: `r page_weight`
description: "World of Tanks Blitz stats. Update `r update`"

tags: [ "`r update`", "Update" ]
autohide: true
hidden: true
alwaysopen: true
---

`r update_if_final(update, "", "_Preliminary stats_")`

Statistics of battles fought during **update `r update``r print_if(preliminary, " so far")`**.
All the stats (WR, damage, battles, etc.) refer to stats during the update, not career stats
unless otherwise mentioned. In total, there were `r auto_format(Battles)` battles by `r auto_format(Players)` players recorded.

## The Best Performing Tanks

### Highest Relative WR

The graph shows the tanks with the highest _Relative WR_. That is the average of players' WR in a tank compared to their average WR at the tier (in all same tier tanks). Relative WR is a measure of the performance/strength of the tank.

{{% expand "Show details" %}}
* All the statistics are about battles fought during the update `r update` only.
* The impact of "Stock-grind battles" is reduced based on tier-specific requirement for total battles at the end of the update. Only players with more than `r floor(min(min_battles.grinds))`-`r floor(max(min_battles.grinds))` (depending on the tier) battles in a tank _in the end of the update_ are included to eliminate the impact of the first battles in the tank (with sub-100% crew / modules).
* The players need to have `r min(min_battles.tanks)`-`r max(min_battles.tanks)` battles in a tank and `r min(min_battles.tiers)`-`r max(min_battles.tiers)` battles at the tier during the update.
* **Average WR** is the players's average WR in the tank
* **Player WR at Tier** is the average WR of the players of the tank at the tier. Since different tiers have different difficulty, it is more meaningful to compare players' performance in the same tier tanks.
* Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.
{{% /expand %}}

```{r fig_tanks_all_Relative_WR_topN}
res <- head(stats.update.perf[DT_filter_enough_battles.rWR(stats.update.perf),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE)
```

#### Highest Relative WR - Table

{{% expand "Show table" %}}
```{r tanks_all_Relative_WR_topN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


### Relative WR by player skill-level

This graph shows the best performing tanks by _Relative WR_ by player skill-levels measured as WR at the tank's tier.

{{% expand "Relative WR - 65%+ players" %}}
```{r fig_tanks_all_Relative_WR_topN_65_}
res <- head(stats.update.perf[
  DT_filter_enough_battles.rWR(stats.update.perf) &
    (WR.tier.maxed > .65),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
title <- get_plot_title_subtitle(title, "Player WR at tier 65%+")
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE)
```
{{% /expand %}}


{{% expand "Relative WR - 55-65% players" %}}
```{r fig_tanks_all_Relative_WR_topN_55_65}
res <- head(stats.update.perf[
  DT_filter_enough_battles.rWR(stats.update.perf) &
    (WR.tier.maxed > .55) & (WR.tier.maxed <= .65),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
title <- get_plot_title_subtitle(title, "Player WR at tier 55-65%")
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE)
```
{{% /expand %}}



{{% expand "Relative WR - 45-55% players" %}}
```{r fig_tanks_all_Relative_WR_topN_45_55}
res <- head(stats.update.perf[
  DT_filter_enough_battles.rWR(stats.update.perf) &
    (WR.tier.maxed > .45) & (WR.tier.maxed <= .55),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
title <- get_plot_title_subtitle(title, "Player WR at tier 45-55%")
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE)
```
{{% /expand %}}


{{% expand "Relative WR - 0-45% players" %}}
```{r fig_tanks_all_Relative_WR_topN_0_45}
res <- head(stats.update.perf[
  DT_filter_enough_battles.rWR(stats.update.perf) &
    (WR.tier.maxed <= .45),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(-`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
title <- get_plot_title_subtitle(title, "Player WR at tier -45%")
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE)
```
{{% /expand %}}


## Highest Average WR

This graph shows the tanks with the highest average WR during update `r update`. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Details" %}}
* Only battles in maxed-out tanks are taken into account. It is assumed that a tank is maxed out if it is a) premium tank or b) player has more than certain number of  battles in it in the end of the update (tier dependent: Tier I: 0 battles, Tier X: `r min_battles.grinds[10]` battles.
* Since the data is fetched once per update, the stats for just released new Tech-Tree tanks is lower than it should be since the battles  players ground the tanks from stock are included in the average.
* On the other hand new high tier tanks are often ground first by more active and also better players that distorts the average WR.
* Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.
{{% /expand %}}


```{r fig_tanks_all_WR_topN}
res <- head(stats.update.perf[, .(
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(-`Average WR`)], n = topN)
res <- prep_plot_tank(res, "Average WR")
title <- get_plot_title_top_tanks("Average WR", topN = topN)
plot_col_discrete_2Y(res, title, update, "Tank", "Average WR", "Player WR", fill_var = "Tank type")
```

#### Highest Average WR - Table

**Average WR** denotes average WR in a tank across all the players during the update. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Show table" %}}
```{r tanks_all_WR_topN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Highest Average Damage (tier-for-tier)

This graph shows the tanks with the highest average damage vs tier average during update `r update`. For the overall highest average damage chart, please see [Tier X Average Damage rankings](10/#highest-average-damage).

```{r fig_tanks_all_avg_dmg_highest}
res <- stats.update.perf[, .(
  "Average Damage" = mean(avg_dmg),
  "Tier" = first(tier),
  "Average WR" = DT_ratio(wins, battles),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium),
  "Vehicle Class" = first(type)
),
by = name
][Players >= min_players.tank][order(-`Average Damage`)]

avg_dmg.tier <- stats.update.perf[DT_filter_enough_battles.tier(stats.update.perf),
  .("Average Damage/Tier" = DT_ratio(damage_dealt, battles)),
  by = .(Tier = tier)
]
setkey(res, Tier)
setkey(avg_dmg.tier, Tier)
res <- merge(res, avg_dmg.tier, all.x = TRUE)

res.highest.avg_dmg_tier <- head(res[, .(name,
  Tier = Tier,
  "Damage/Tier Average %" = `Average Damage` / `Average Damage/Tier` - 1, `Average Damage`,
  `Average WR`, Players, `Vehicle Class`, `Premium`
)][order(-`Damage/Tier Average %`)], topN)
res.lowest.avg_dmg_tier <- head(res[, .(name,
  Tier = Tier,
  "Damage/Tier Average %" = `Average Damage` / `Average Damage/Tier` - 1, `Average Damage`,
  `Average WR`, Players, `Vehicle Class`, `Premium`
)][order(`Damage/Tier Average %`)], topN)
x_name <- "Tank"
y_name <- "Damage/Tier Average %"
y2_name <- "Players"
var_fill <- "Tank type"
res <- prep_plot_tank(res.highest.avg_dmg_tier, y_name)
title <- get_plot_title_top_tanks("Average Damage (tier-for-tier)", top = TRUE, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = var_fill, y2_pct = FALSE)
```

#### Highest Average Damage (tier-for-tier) - Table

{{% expand "Show table" %}}
```{r tanks_all_avg_dmg_highest, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Highest Average Kills/Battle

This graph shows the tanks with the most kills per battle on average WR during update `r update`. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Details" %}}
* Only battles in maxed-out tanks are taken into account. It is assumed that a tank is maxed out if it is a) premium tank or b) player has more than certain number of  battles in it in the end of the update (tier dependent: Tier I: 0 battles, Tier X: `r min_battles.grinds[10]` battles.
* Since the data is fetched once per update, the stats for just released new Tech-Tree tanks is lower than it should be since the battles  players ground the tanks from stock are included in the average.
* On the other hand new high tier tanks are often ground first by more active and also better players that distorts the stats for those.
* Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.
{{% /expand %}}


```{r fig_tanks_all_avg_kills_topN}
x_name <- "Tank"
y_name <- "Average Kills/Battle"
top <- TRUE

res <- head(stats.update.perf[, .(
  "Average Kills/Battle" = mean(avg_kills),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(-`Average WR`)], n = topN)
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, topN = topN, top = top)

plot_col_discrete_2Y(res, title, update, x_name, y_name, "Player WR",
  fill_var = "Tank type",
  y_pct = FALSE, y_step = 0.2, top = top
)
```

#### Highest Average Kills/Battle - Table

{{% expand "Show table" %}}

**Average WR** denotes average WR in a tank across all the players during the update. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

```{r tanks_all_avg_kills_topN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}



## Highest Spot Rate

```{r fig_tanks_all_spot_rate_topN}
res <- head(stats.update.perf[, .(
  "Spot Rate" = mean(spot_rate),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(-`Spot Rate`)], n = topN)
x_name <- "Tank"
y_name <- "Spot Rate"
y2_name <- "Average WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y_pct = FALSE, y_step = 0.2)
```

#### Highest Spot Rate - Table

{{% expand "Show table" %}}
```{r tanks_all_spot_rate_topN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Highest Hit Rate

```{r fig_tanks_all_hit_rate_topN}
res <- head(stats.update.perf[, .(
  "Hit Rate" = mean(hit_rate, na.rm = TRUE),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(-`Hit Rate`)], n = topN)
x_name <- "Tank"
y_name <- "Hit Rate"
y2_name <- "Average WR"
top <- TRUE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = top, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name,
  fill_var = "Tank type",
  y_pct = TRUE, y_step = 0.2, top = top
)
```

#### Highest Hit Rate - Table

{{% expand "Show table" %}}
```{r tanks_all_hit_rate_topN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Most Popular Tanks

This graph shows the most popular tanks by the number of players during the update `r update`.

```{r fig_tanks_all_most_popular}
res <- head(stats.update[, .(
  "Average WR" = mean(WR),
  "Battles/Player" = mean(battles),
  "Players" = uniqueN(account_id),
  "Premium" = first(is_premium)
),
by = name
][order(-Players)], n = topN)
x_name <- "Tank"
y_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Tank type", y_pct = FALSE, y_step = 20e3)
```

####  Most popular Tanks - Table

{{% expand "Show table" %}}
```{r tanks_all_most_popular, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Most played tanks

This graph shows the most played tanks by number of battles during the update `r update`.

```{r fig_tanks_all_most_played}
res <- head(stats.update[, .(
  "Average WR" = mean(WR),
  "Battles" = sum(battles),
  "Battles/Player" = mean(battles),
  "Players" = uniqueN(account_id),
  "Premium" = first(is_premium)
),
by = name
][order(-Battles)], n = topN)
x_name <- "Tank"
y_name <- "Battles"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = TRUE, topN = topN)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Tank type", y_pct = FALSE, y_step = 500e3)
```

####  Most Played Tanks - Table

{{% expand "Show table" %}}
```{r tanks_all_most_played, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}

# Lowest Performing Tanks

## Lowest Relative WR

The graph shows the tanks with the lowest _Relative WR_. That is the average of players' WR in a tank compared to their average WR at the tier (in all same tier tanks). Relative WR is a measure of the performance/strength of the tank.

{{% expand "Show details" %}}
* All the statistics are about battles fought during the update `r update` only.
* The impact of "Stock-grind battles" is reduced based on tier-specific requirement for total battles at the end of the update. Only players with more than `r floor(min(min_battles.grinds))`-`r floor(max(min_battles.grinds))` (depending on the tier) battles in a tank _in the end of the update_ are included to eliminate the impact of the first battles in the tank (with sub-100% crew / modules).
* The players need to have `r min(min_battles.tanks)`-`r max(min_battles.tanks)` battles in a tank and `r min(min_battles.tiers)`-`r max(min_battles.tiers)` battles at the tier during the update.
* **Average WR** is the players's average WR in the tank
* **Player WR at Tier** is the average WR of the players of the tank at the tier. Since different tiers have different difficulty, it is more meaningful to compare players' performance in the same tier tanks.
{{% /expand %}}

```{r fig_tanks_all_Relative_WR_bottomN}
res <- head(stats.update.perf[DT_filter_enough_battles.rWR(stats.update.perf),
  .(
    "Average WR" = mean(WR),
    "Relative WR" = mean(rWR),
    "Player WR at Tier" = mean(WR.tier.maxed),
    "Players" = uniqueN(account_id),
    "Battles/Player" = mean(battles),
    "Premium" = first(is_premium)
  ),
  by = name
][Players >= min_players.tank][order(`Relative WR`)], n = topN)
x_name <- "Tank"
y_name <- "Relative WR"
y2_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, topN = topN, top = FALSE)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = "Tank type", y2_pct = FALSE, top = FALSE)
```

#### Lowest Relative WR - Table

{{% expand "Show table" %}}
```{r tanks_all_Relative_WR_bottomN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Lowest Average WR

This graph shows the tanks with the lowest average WR during update `r update`. **Player WR** denotes the tank's players' average WR across all the tanks during the update. Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.

```{r fig_tanks_all_WR_bottomN}
res <- head(stats.update.perf[, .(
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(`Average WR`)], n = topN)
res <- prep_plot_tank(res, "Average WR")
title <- get_plot_title_top_tanks("Average WR", topN = topN, top = FALSE)
plot_col_discrete_2Y(res, title, update, "Tank", "Average WR", "Player WR", fill_var = "Tank type", top = FALSE)
```

#### Lowest Average WR - Table

**Average WR** denotes average WR in a tank across all the players during the update. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Show table" %}}
```{r tanks_all_WR_bottomN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Lowest Average Damage (tier-for-tier)

This graph shows the tanks with the lowest average damage vs tier average during update `r update`.

```{r fig_tanks_all_avg_dmg_lowest}
## res.lowest.avg_dmg_tier set up earlier
x_name <- "Tank"
y_name <- "Damage/Tier Average %"
y2_name <- "Players"
var_fill <- "Tank type"
res <- prep_plot_tank(res.lowest.avg_dmg_tier, y_name)
title <- get_plot_title_top_tanks("Average Damage (tier-for-tier)", top = FALSE, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name, fill_var = var_fill, y_step = 0.05, y2_pct = FALSE, top = FALSE)
```


#### Lowest Average Damage (tier-for-tier) - Table

{{% expand "Show table" %}}
```{r tanks_all_avg_dmg_lowes, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Lowest Average Kills/Battle

This graph shows the tanks with the most kills per battle on average WR during update `r update`. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

{{% expand "Details" %}}
* Only battles in maxed-out tanks are taken into account. It is assumed that a tank is maxed out if it is a) premium tank or b) player has more than certain number of  battles in it in the end of the update (tier dependent: Tier I: 0 battles, Tier X: `r min_battles.grinds[10]` battles.
* Since the data is fetched once per update, the stats for just released new Tech-Tree tanks is lower than it should be since the battles  players ground the tanks from stock are included in the average.
* On the other hand new high tier tanks are often ground first by more active and also better players that distorts the stats for those.
* Only tanks with more than `r min_players.tank` players are listed. This may filter out few upcoming tanks that are being tested.
{{% /expand %}}


```{r fig_tanks_all_avg_kills_bottomN}
x_name <- "Tank"
y_name <- "Average Kills/Battle"
top <- FALSE

res <- head(stats.update.perf[, .(
  "Average Kills/Battle" = mean(avg_kills),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(`Average WR`)], n = topN)
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, topN = topN, top = top)

plot_col_discrete_2Y(res, title, update, x_name, y_name, "Player WR",
  fill_var = "Tank type",
  y_pct = FALSE, y_step = 0.1, top = top
)
```

#### Lowest Average Kills/Battle - Table

{{% expand "Show table" %}}

**Average WR** denotes average WR in a tank across all the players during the update. **Player WR** denotes the tank's players' average WR across all the tanks during the update.

```{r tanks_all_avg_kills_bottomN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Lowest Spot Rate

```{r fig_tanks_all_spot_rate_bottomN}
N <- 20
res <- head(stats.update.perf[, .(
  "Spot Rate" = mean(spot_rate),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(`Spot Rate`)], n = topN)
x_name <- "Tank"
y_name <- "Spot Rate"
y2_name <- "Average WR"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = FALSE, topN = topN)
plot_col_discrete_2Y(res, title, update,
  x_name = x_name, y_name = y_name, y2_name = y2_name, fill_var = "Tank type",
  y_step = 0.1, y_pct = FALSE, top = FALSE
)
```

#### Lowest Spot Rate - Table

{{% expand "Show table" %}}
```{r tanks_all_spot_rate_bottomN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Lowest Hit Rate

```{r fig_tanks_all_hit_rate_bottomN}
res <- head(stats.update.perf[, .(
  "Hit Rate" = mean(hit_rate, na.rm = TRUE),
  "Average WR" = mean(WR),
  "Player WR" = mean(WR.update),
  "Players" = uniqueN(account_id),
  "Battles/Player" = mean(battles),
  "Premium" = first(is_premium)
),
by = name
][Players >= min_players.tank][order(`Hit Rate`)], n = topN)
x_name <- "Tank"
y_name <- "Hit Rate"
y2_name <- "Average WR"
top <- FALSE
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = top, topN = topN)
plot_col_discrete_2Y(res, title, update, x_name, y_name, y2_name,
  fill_var = "Tank type",
  y_pct = TRUE, y_step = 0.2, top = top
)
```

#### Lowest Hit Rate - Table

{{% expand "Show table" %}}
```{r tanks_all_hit_rate_bottomN, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}


## Least Popular Tanks

This graph shows the least popular tanks by the number of players during the update `r update`. The graph includes also unreleased tanks in super-testing.

```{r fig_tanks_all_least_popular}
res <- head(stats.update[, .(
  "Average WR" = mean(WR),
  "Battles/Player" = mean(battles),
  "Players" = uniqueN(account_id),
  "Premium" = first(is_premium)
),
by = name
][order(Players)], n = topN)
x_name <- "Tank"
y_name <- "Players"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, top = FALSE, topN = topN)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Tank type", y_pct = FALSE, top = FALSE)
```


#### Least Played Tanks - Table

{{% expand "Show table" %}}
```{r tanks_all_least_popular, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}

## Least played tanks

This graph shows the most played tanks by number of battles during the update `r update`.

```{r fig_tanks_all_least_played}
res <- head(stats.update[, .(
  "Average WR" = mean(WR),
  "Battles" = sum(battles),
  "Battles/Player" = mean(battles),
  "Players" = uniqueN(account_id),
  "Premium" = first(is_premium)
),
by = name
][order(Battles)], n = topN)
x_name <- "Tank"
y_name <- "Battles"
res <- prep_plot_tank(res, y_name)
title <- get_plot_title_top_tanks(y_name, topN = topN, top = FALSE)
plot_col_discrete_1Y(res, title, update, x_name, y_name, fill_var = "Tank type", y_pct = FALSE, top = FALSE)
```

#### Least Played Tanks - Table

{{% expand "Show table" %}}
```{r tanks_all_least_played, echo = FALSE}
md_table(res, update_path_lvl = 0, enough_players = tanks.enough_players)
```
{{% /expand %}}

```{r clean_up, include=FALSE}
rm(list = var2rm)
gc(verbose = FALSE)
```
