---
title: "Update 7.9 final stats added "
linktitle: "2021-06-11 Update 7.9 final stats added"
date: `r today("UTC")`
publishdate: 2021-06-11
author: Jylpah@gmail.com
disableToc: false
output: md_document
alwaysopen: false
hidden: true
tags: [ "post", "7.9" ]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, dpi= 150, echo = FALSE, dev = 'svglite', fig.ext = 'svgz');
update_ver = '7.9'
stopifnot(all(exists("stats.update"), update_ver == update))
res <- stats.update[, .(Battles=sum(all.battles), Players=uniqueN(account_id))]
stats.update.perf <- get_stats_tank_perf.rWR(stats.update)

```

Final stats for `r md_link_update(update=update_ver)` have been added. 

* In total, there were 199M battles by 492k players recorded in the database during 
the `r md_link_update(update=update_ver)`.

* It is getting boring the report the best performing tanks - the same ones keep 
topping the charts update after update in slightly different order:  
1) `r md_link_tank(tank_names='Annihilator', update=update_ver)`, 
2) `r md_link_tank(tank_names='Object 252U', update=update_ver)`, 
3) `r md_link_tank(tank_names='T54E2', update=update_ver)`,  
4) `r md_link_tank(tank_names='T28 Concept', update=update_ver)` and 
5) `r md_link_tank(tank_names='Chimera', update=update_ver)`.


```{r fig_tanks_top_RelativeWR}
plot_relativeWR(stats = stats.update.perf, update = update_ver);
```

* `r md_link_update(update=update_ver)` did not have any major 
balance changes. Does it mean WG thinks the game balance is great? 
(Thinking of `r md_link_tank(tank_names='Annihilator', update=update_ver)`) 

* The American experimental heavy tank line leading to 
`r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` 
continues to be super-tested at the moment by all-but-average players: 

```{r fig_tank_player_base_M_VI_Yoh}
tank_id     <- get_tank_id('M-VI-Yoh')
tank_type  	<- get_tank_type(tank_id)
tank_types  <- paste0(tank_type, 's')
tierN 			<- get_tank_tier(tank_id)
stats 			<- get_stats.update.tier.type(DT = stats.update.perf, tierN = tierN,
																					tank_type = tank_type)
plot_tank_player_base(stats = stats, tank_id = tank_id, 
                      title.avg = paste('Tier', get_tier_roman(tierN), tank_types), 
                      update = update_ver)
```

While the `r md_link_tank(tank_names='M-VI-Yoh', update=update_ver)` 
players are super unicums, the tank seems to perform extremely well for 
the super-testers even by their own standards. And the early YouTuber 
reviews indicate the tank was  released as ... very-good.  

```{r fig_tank_relativeWR_M_VI_Yoh}
tank_id     <- get_tank_id('M-VI-Yoh')
tierN 			<- get_tank_tier(tank_id)
stats 			<- get_stats.update.tier.type(DT = stats.update.perf, tierN = tierN,
																					tank_type = tank_type)
plot_tank_relativeWR(stats = stats, tank_id = tank_id, update = update_ver)
```
